---
layout:     post
author:		Najko Jahn
title:      Justus Liebig University Giessen joins OpenAPC!
date:       2015-06-19 14:21:29
summary:    
categories: general
comments: true
---

```{r, echo =FALSE}

knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

[Justus Liebig University Giessen](https://www.uni-giessen.de/cms/welcome?set_language=en) supports the publication of research findings in Open Access journals through its [OA Publication Fund](https://www.uni-giessen.de/ub/en/digitales-publizieren-en/openaccess-en/oafonds-en?set_language=en). The fund has been financially supported by the DFG [Open-Access Publishing Programme](http://www.dfg.de/en/research_funding/programmes/infrastructure/lis/funding_opportunities/open_access_publishing/index.html) since 2011.

Contact person is Florian Ruckelshausen <mailto:openaccess@bibsys.uni-giessen.de>.

### Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$Institution == "Giessen U",]
my.apc <- droplevels(my.apc)
```

The data set covers publication fees for `r nrow(my.apc)` Open Access journal articles. Total expenditure is `r sum(my.apc$EURO)`€ and the average fee paid `r sum(my.apc$EURO)/nrow(my.apc)`€.

### Fees paid per publisher (in €)

```{r tree_jlu, echo=FALSE, message = FALSE}
tt <- aggregate(my.apc$EURO, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in €)

```{r box_jlu_year, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(Period), EURO)) + geom_boxplot() + geom_point(alpha = 8/10, size = 2,aes(colour =is_hybrid)) + scale_colour_manual(values = c("#000A02", "#DC4E00"))
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in €)

```{r box_jlu_publisher, echo = FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(publisher, EURO)) + geom_boxplot() + geom_point(alpha = 8/10, size = 2,aes(colour =is_hybrid)) + scale_colour_manual(values = c("#000A02", "#DC4E00"))

q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 9) + coord_flip()
q + xlab("Publisher") + ylab("APC")
```
