---
layout:     post
author:		Najko Jahn
title:      MDC Berlin joins OpenAPC!
date:       2015-05-15 11:21:29
summary:    
categories: general
comments: true
---

```{r, echo =FALSE}

knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```


The [Max Delbrück Center for Molecular Medicine (MDC)](https://www.mdc-berlin.de/en) has joined [openapc.github.io](https://openapc.github.io) and is sharing its expenditures for publications in both Open Access and toll-access journals.

Contact person is [Dr.Dorothea Busjahn](https://www.mdc-berlin.de/1161898/de/about_the_mdc/structure/administration/library/teammember).

### Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$Institution == "MDC",]
my.apc <- droplevels(my.apc)
my.hybrid <- my.apc[my.apc$is_hybrid == TRUE,]
my.oa <- my.apc[my.apc$is_hybrid == FALSE,]
```

#### Open Access

The data set covers publication fees for `r nrow(my.oa)` Open Access journal articles paid in 2014. Total expenditure was `r sum(my.oa$EURO)`€ and the average fee paid `r sum(my.oa$EURO)/nrow(my.apc)`€.

#### Hybrid 

In many toll-access journals some of the articles are open access after a fee has been paid. This model is often called "hybrid open access". The dataset covers `r nrow(my.hybrid)` hybrid open access articles. Total expenditure amounts to `r format(sum(my.hybrid$EURO), scientific=FALSE)`€. Average fee is `r format(sum(my.hybrid$EURO)/nrow(my.hybrid), digits = 5)`€ and the median `r median(my.hybrid$EURO)`€.


### Fees paid per publisher

```{r tree_MDC, echo=FALSE, message = FALSE}
tt <- aggregate(my.apc$EURO, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year

```{r box_MDC_year, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(Period), EURO)) + geom_boxplot() + geom_point(alpha = 8/10, size = 2,aes(colour =is_hybrid)) + scale_colour_manual(values = c("#000A02", "#DC4E00"))
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher

```{r box_MDC_publisher, echo = FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(publisher, EURO)) + geom_boxplot() + geom_point(alpha = 8/10, size = 2,aes(colour =is_hybrid)) + scale_colour_manual(values = c("#000A02", "#DC4E00"))

q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher") + ylab("APC")
```
