---
layout:     post
author:    Najko Jahn
title:      TU Chemnitz releases its 2015 expenditure
date:       2015-12-09 16:21:29
summary:    
categories: general
comments: true
---


```{r, echo =FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

[Technische Universität Chemnitz](https://www.tu-chemnitz.de/) has contributed its cost information for 2015. Chemnitz University Library is in charge of the [University's Open Access Publishing Fund](https://www.tu-chemnitz.de/ub/publizieren/openaccess/publikationsfonds.html), which is supported under the [DFG's Open Access Publishing Programme](http://www.dfg.de/en/research_funding/programmes/infrastructure/lis/funding_opportunities/open_access_publishing/index.html).

Contact person is Ute Blumtritt <mailto:ute.blumtritt@bibliothek.tu-chemnitz.de>

## About the dataset

The present dataset contains information on publication fees paid in 2014 and 2015. 

## Cost Data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$Institution == "TU Chemnitz",]
my.apc <- droplevels(my.apc)
```

The data set covers publication fees for `r nrow(my.apc)` Open Access journal articles. Total expenditure is `r sum(my.apc$EURO)`€ and the average fee paid `r sum(my.apc$EURO)/nrow(my.apc)`€.

### Fees paid per publisher (in €)

```{r tree_tuchemnitz15, echo=FALSE, message = FALSE}
tt <- aggregate(my.apc$EURO, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in €)

```{r box_tuchemnitz15_year, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(Period), EURO)) + geom_boxplot() + geom_point(alpha = 8/10, size = 2,aes(colour =is_hybrid)) + scale_colour_manual(values = c("#000A02", "#DC4E00"))
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in €)

```{r box_tuchemnitz15_publisher, echo = FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(publisher, EURO)) + geom_boxplot() + geom_point(alpha = 8/10, size = 2,aes(colour =is_hybrid)) + scale_colour_manual(values = c("#000A02", "#DC4E00"))

q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 9) + coord_flip()
q + xlab("Publisher") + ylab("APC")
```
