---
layout:     post
author:    Najko Jahn
title:      University Library Heidelberg joins OpenAPC
date:       2015-03-19 09:21:29
summary:    
categories: general
comments: true
---


```{r, echo =FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

We welcome [University Library Heidelberg](http://www.ub.uni-heidelberg.de/Englisch/Welcome.html) as our new contributing institution. [University Library Heidelberg](http://www.ub.uni-heidelberg.de/Englisch/Welcome.html) is in charge of the [Heidleberg University Open Access Publishing Fund](http://www.ub.uni-heidelberg.de/Englisch/service/openaccess/publikationsfonds.html).

Contact person is Dr. Jochen Apel, Heidelberg University Library, 0049(0)6221-54-4249, <apel@ub.uni-heidelberg.de>.

## About the dataset

The present dataset contains information on publication fees paid from the budget of Heidelberg University's open access publishing fund for 2014. The fund is part of [DFG’s Open Access Publishing Programme](http://www.dfg.de/en/research_funding/programmes/infrastructure/lis/funding_opportunities/open_access/).  Due to a pre-pay membership with BioMed Central (leading to a discount of 20% on publication fees from this publisher) a few funding applications from 2014 are still pending, because the respective article manuscripts are still under review. Nevertheless the corresponding financial resources were spent already in 2014 in order to top up the BioMed Central membership account. Thus, the present dataset for 2014 is not complete yet. Comprehensive data will be released as soon as possible. For more information please see the [fund's website](http://www.ub.uni-heidelberg.de/Englisch/service/openaccess/publikationsfonds.html).

## Cost Data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$Institution == "Heidelberg U",]
my.apc <- droplevels(my.apc)
```

The dataset covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles, which the fund covered in 2014 so far. Total expenditure amounts to `r sum(my.apc$EURO)`€ and the average fee is `r sum(my.apc$EURO)/nrow(my.apc)`€.

The following table shows the payments the [University Library Heidelberg](http://www.ub.uni-heidelberg.de/Englisch/Welcome.html) has made to the publishers (including taxes)

```{r}
my.apc$publisher <- factor(my.apc$publisher, 
                           levels =  c(rownames(data.frame(rev(sort(table(my.apc$publisher)))))))

df.summary <-cbind(tapply(my.apc$EURO, my.apc$publisher, length),
             tapply(my.apc$EURO, my.apc$publisher, sum),
             tapply(my.apc$EURO, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Fees paid per publisher (in EURO)

```{r tree_heidi}
tt <- aggregate(my.apc$EURO, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_heidi_year, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(Period), EURO)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_heidi_publisher, echo = FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(publisher, EURO)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher") + ylab("APC")
```
