---
layout:     post
author:		Christoph Broschinski
title:      Leibniz Association's open access fund updates its 2016 APC data
date:       2016-06-23 12:00:00
summary:    
categories: [general, openAPC]
comments: true
---

```{r, echo =FALSE}

knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

The [Open Access Publishing Fund](http://www.leibniz-gemeinschaft.de/en/infrastructures/open-access/open-access-publishing-fund/) of the Leibniz Association has updated its APC expenditures. The latest contribution provides additional data for the 2016 period.

Data is provided by Technische Informationsbibliothek (TIB) – German National Library of Science and Technology. TIB is operating the open access fund together with ZB MED – Leibniz Information Centre for Life Sciences and ZBW – German National Library of Economics – Leibniz Information Centre for Economics.

For 2016, the publishing fund is funded by resources from the strategy fund of the Leibniz Association Executive Board in the amount of  200,000 €. 

## Cost Data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "Leibniz-Fonds", ]
my.apc <- droplevels(my.apc)
```

The new dataset covers additional publication fees for 30 articles covered by the fund in 2016 YTD.

Please note that APCs exceeding 2,000 EUR are shared between the fund and the corresponding Leibniz institution and that this data set only covers payments made via the [central open access publishing fund](http://www.leibniz-gemeinschaft.de/en/infrastructures/open-access/open-access-publishing-fund/).

With the recent contribution included, total expenditure for the 2016 period amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€. The following table provides an overview:

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

