---
layout:     post
author:     Christoph Broschinski
title:      Jisc collections data included into OpenAPC
date:       2016-12-16 07:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```
[Jisc Collections](https://www.jisc-collections.ac.uk/Jisc-Monitor/APC-data-collection/) has been gathering and openly releasing data on APC payments made by UK higher education institutions (HEIs).

One of these datasets (APC data for the 2014 period) has now been included into OpenAPC.

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc_jisc_2014 <- download_apc("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/jisc_collections/final/APCs2014combined_final.csv")
my.apc_jisc_2015 <- download_apc("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/jisc_collections/final/APCs2014combined_paid_in_2015_final.csv")
my.apc = rbind(my.apc_jisc_2014, my.apc_jisc_2015)
my.apc <- my.apc[!is.na(my.apc$institution),]

```
The ingested data covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles published by 22 UK institutions in 2014. Total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€.

The following table and plots show a breakdown of the payments.

### Overview

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Fees paid per publisher (in EURO)

```{r tree_jisc_2016_12_16_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_jisc_2016_12_16_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```
