---
layout:     post
author:     Christoph Broschinski
title:      Max Planck Digital Library updates its 2016 expenditures
date:       2017-01-10 09:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```
The [Max Planck Digital Library (MPDL)](https://www.mpdl.mpg.de/en/) has updated its APC expenditures for the New Journal of Physics in the second half of 2016.

MPDL provides [institutional funding for Open Access publications](https://www.mpdl.mpg.de/en/?id=50:open-access-publishing&catid=17:open-access) for researchers affiliated with the  [Max Planck Society](http://www.mpg.de/en). MPDL makes use of central agreements with Open Access publishers.

Please note that article processing charges funded locally by Max Planck Institutes are not part of this data set. The Max Planck Society has a limited input tax reduction. The refund of input VAT for APC is 20%.

## Cost data


```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc_2016_njp <- my.apc[my.apc$institution == "MPG" & my.apc$period == 2016 & my.apc$journal_full_title %in% c("New Journal of Physics"),]
my.apc_2016_njp <- droplevels(my.apc_2016_njp)
```

The new data covers additional publication fees for 29 NJP articles published by MPG researchers, which MPDL covered in 2016. Together with the [previous APC data](https://openapc.github.io/general/openapc/2016/12/13/mpdl) MPDL's total expenditure for the NJP in 2016 amounts to `r sum(my.apc_2016_njp$euro)`€ and the average fee is `r sum(my.apc_2016_njp$euro)/nrow(my.apc_2016_njp)`€.


## Overview

With the recent contributions included, the overall APC data for the MPDL now looks as follows:

### Fees paid per publisher (in EURO)

```{r tree_mpdl_2017_01_10_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_mpdl_2017_01_10_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```
