---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      Max Planck Digital Library reports 2016 expenditures for various publishers
date:       2017-08-10 08:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

The [Max Planck Digital Library (MPDL)](https://www.mpdl.mpg.de/en/) has reported its 2016 expenditures for PLoS, Frontiers, SPIE, eLife and Copernicus journals.

MPDL provides [institutional funding for Open Access publications](https://www.mpdl.mpg.de/en/?id=50:open-access-publishing&catid=17:open-access) for researchers affiliated with the [Max Planck Society](http://www.mpg.de/en). MPDL makes use of central agreements with Open Access publishers.

Please note that article processing charges funded locally by Max Planck Institutes are not part of this data set. The Max Planck Society has a limited input tax reduction. The refund of input VAT for APC is 20%.

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}


my.apc_multiple_16 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/mpg/openapc_mpg_frontiers_2016_enriched.csv"))

my.apc_plos_16 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/mpg/openapc_mpg_plos_2016_enriched.csv"))
my.apc_copernicus_16 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/mpg/openapc_mpg_copernicus_201701-06_enriched.csv"))
my.apc_spie_16 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/mpg/openapc_mpg_spie_2016_enriched.csv"))
my.apc_elife_16 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/mpg/openapc_mpg_elife_2017_20170712_enriched.csv"))

my.apc_multiple_16 <- rbind(my.apc_multiple_16, my.apc_plos_16)
my.apc_multiple_16 <- rbind(my.apc_multiple_16, my.apc_copernicus_16)
my.apc_multiple_16 <- rbind(my.apc_multiple_16, my.apc_spie_16)
my.apc_multiple_16 <- rbind(my.apc_multiple_16, my.apc_elife_16)

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "MPG",]
my.apc <- droplevels(my.apc)
```

The new dataset covers publication fees for `r format(nrow(my.apc_multiple_16), big.mark =",")` articles published by MPG researchers in the aforementioned journals. Total expenditure amounts to `r sum(my.apc_multiple_16$euro)`€ and the average fee is `r sum(my.apc_multiple_16$euro)/nrow(my.apc_multiple_16)`€.

```{r}
d_frame = data.frame(table(my.apc_multiple_16$journal_full_title,  dnn="Journal"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Journal)), ]                                           
                                    
my.apc_multiple_16$journal_full_title <- factor(my.apc_multiple_16$journal_full_title, levels =  d_frame$Journal)

df.summary <-cbind(tapply(my.apc_multiple_16$euro, my.apc_multiple_16$journal_full_title, length),
             tapply(my.apc_multiple_16$euro, my.apc_multiple_16$journal_full_title, sum),
             tapply(my.apc_multiple_16$euro, my.apc_multiple_16$journal_full_title, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

## Overview

With the recent contribution included, the overall APC data for the MPG now looks as follows:

### Fees paid per publisher (in EURO)

```{r tree_mpdl_2017_08_10_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_mpdl_2017_08_10_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_mpdl_2017_08_10_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 2])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 2 articles)") + ylab("APC")
```
