---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      Couperin.org provides additional APC data for two institutions
date:       2018-09-05 08:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

The [Couperin consortium](https://couperin.org) collects data on APC expenditures from universities and other research institutions in France. The latest data delivery contains additional articles for the Université de Bourgogne and an initial data set for the Université Paris Descartes.

Contact Persons for Couperin are [Valerie Larroque](mailto:valerie.larroque@couperin.org) and [Sandrine Malotaux](mailto:sandrine.malotaux@inp-toulouse.fr).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc_bourgogne <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/61785cae6798f204cb59f45641981be5daec88c8/data/couperin/bourgogne/OpenAPC_donn%C3%A9es2015_Bourgogne_enriched.csv"))
my.apc_bourgogne <- my.apc_bourgogne[9:15,]
my.apc_paris <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/couperin/paris-descartes/OpenAPC_donn%C3%A9es2015_Paris-Descartes_enriched.csv"))
my.apc <- rbind(my.apc_bourgogne, my.apc_paris)
my.apc <- droplevels(my.apc)
```

The new data set provided by Couperin covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles published in 2015. Total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€.

The data originates from the Université de Bourgogne (Update) and the Université Paris Descartes (Initial data).


```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

## Overview

A detailed analysis of the contributed data provides the following overview:

### Fees paid per publisher (in EURO)

```{r tree_couperin_2018_09_05_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per publisher (in EURO)

```{r box_couperin_2018_09_05_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 2])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 2 articles )") + ylab("APC")
```
