---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      Leibniz Association's open access fund reports its 2017 APC expenditures
date:       2018-01-15 12:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

The [Open Access Publishing Fund](http://www.leibniz-gemeinschaft.de/en/infrastructures/open-access/open-access-publishing-fund/) of the Leibniz Association has updated its APC expenditures for the 2017 period.

Data is provided by Technische Informationsbibliothek (TIB - German National Library of Science and Technology). TIB is operating the open access fund together with ZB MED (Leibniz Information Centre for Life Sciences) and ZBW (German National Library of Economics – Leibniz Information Centre for Economics).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "Leibniz-Fonds",]
my.apc <- droplevels(my.apc)
my.apc_2017 <- my.apc[my.apc$period == 2017,]
my.apc_2017 <- droplevels(my.apc_2017)
```

The new dataset covers publication fees for `r format(nrow(my.apc_2017), big.mark =",")` articles. Total expenditure amounts to `r sum(my.apc_2017$euro)`€ and the average fee is `r sum(my.apc_2017$euro)/nrow(my.apc_2017)`€.

To interpret the cost data correctly, please have a look at the [funding policy](https://github.com/OpenAPC/openapc-de/blob/master/data/leibnizfonds/README.md) of the Leibniz Association's open access fund.

```{r}
d_frame = data.frame(table(my.apc_2017$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_2017$publisher <- factor(my.apc_2017$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_2017$euro, my.apc_2017$publisher, length),
             tapply(my.apc_2017$euro, my.apc_2017$publisher, sum),
             tapply(my.apc_2017$euro, my.apc_2017$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

## Overview

With the recent contribution included, the overall APC data for the Leibniz Association's open access fund now looks as follows:

### Fees paid per publisher (in EURO)

```{r tree_leibnizfonds_2018_01_15_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_leibnizfonds_2018_01_15_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_leibnizfonds_2018_01_15_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 5])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 5 articles)") + ylab("APC")
```
