---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      Jisc collections data for 2017 ingested
date:       2018-11-15 07:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

[Jisc Collections](https://www.jisc-collections.ac.uk/Jisc-Monitor/APC-data-collection/) has been gathering and releasing data on APC payments made by UK higher education institutions (HEIs).

Aggregated data for the last year has been made available recently and is now included into OpenAPC. 

Since the data format employed by Jisc differs from the OpenAPC standard in several ways, a comprehensive pre- and postprocessing had to be conducted. The [README](https://github.com/OpenAPC/openapc-de/tree/master/data/jisc_collections/2017) in the Jisc data folder provides more details.

## New ingestion

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc_new <- download_apc("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/jisc_collections/2017/postprocessed/Jisc_2017_postprocessed.csv")
my.apc_new <- my.apc_new[!(is.na(my.apc_new$institution)),]
my.apc_new <- droplevels(my.apc_new)

my.apc_old <- download_apc("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/jisc_collections/2014-2016/postprocessed/ALLAPCDATAMERGEDpublicwithnotes_final.csv")
my.apc_old <- my.apc_old[!(is.na(my.apc_old$institution)),]
my.apc_old <- droplevels(my.apc_old)

my.apc_rec <- download_apc("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/jisc_collections/2014-2016/reconstructed_doi_articles/postprocessed/jisc_dois_imported_postprocessed.csv")
my.apc_rec <- my.apc_rec[!(is.na(my.apc_rec$institution)),]
my.apc_rec <- droplevels(my.apc_rec)

my.apc_all <- rbind(my.apc_new, my.apc_old, my.apc_rec)

```

The ingested data covers publication fees for `r format(nrow(my.apc_new), big.mark =",")` articles published by UK institutions. Total expenditure amounts to `r sum(my.apc_new$euro)`€ and the average fee is `r sum(my.apc_new$euro)/nrow(my.apc_new)`€.

The following table shows a breakdown, grouped by publishers.

```{r}
d_frame = data.frame(table(my.apc_new$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_new$publisher <- factor(my.apc_new$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_new$euro, my.apc_new$publisher, length),
             tapply(my.apc_new$euro, my.apc_new$publisher, sum),
             tapply(my.apc_new$euro, my.apc_new$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

## Jisc data 

With the new data set included, the whole Jisc collections data ingested by OpenAPC up to now (`r format(nrow(my.apc_all), big.mark =",")` articles) looks as follows:

### Fees paid per publisher (in EURO)

```{r tree_jisc_2018_11_15_full}
tt <- aggregate(my.apc_all$euro, by = list(my.apc_all$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_jisc_2018_11_15_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc_all, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_jisc_2018_11_15_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc_all$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 300])
my.apc_reduced = my.apc_all[my.apc_all$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 300 articles)") + ylab("APC")
```
