---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      2017 data for several French institutions contributed by Couperin.org
date:       2018-11-22 08:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

The [Couperin consortium](https://couperin.org) collects data on APC expenditures from universities and other research institutions in France. 

A large batch of APC data for the 2017 period has now been made available to OpenAPC, containing articles from 17 different institutions (with 5 contributing for the first time).

Contact Persons for Couperin are [Valerie Larroque](mailto:valerie.larroque@couperin.org) and [Sandrine Malotaux](mailto:sandrine.malotaux@inp-toulouse.fr).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$period == 2017 & my.apc$institution %in% c("Université de Nantes", "Ecole normale supérieure de Paris", "ESPCI Paris", "Institut national polytechnique de Toulouse", "Aix-Marseille Université", "Université d'Avignon et des Pays de Vaucluse", "Université de Bourgogne", "Université de Caen Normandie", "Université Clermont Auvergne", "Université de Poitiers", "Université Nice-Sophia-Antipolis", "Université de Rennes 1", "Université de Toulon", "CIRAD", "INSERM", "Institut de recherche pour le développement (IRD)", "Université d'Angers"),]
my.apc <- droplevels(my.apc)
```

The new data set provided by Couperin covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles published in 2017. Total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€.

The data originates from the following institutions:

- Université de Nantes
- Ecole normale supérieure de Paris
- ESPCI Paris
- Institut national polytechnique de Toulouse
- Aix-Marseille Université
- Université d'Avignon et des Pays de Vaucluse
- Université de Bourgogne
- Université de Caen Normandie
- Université Clermont Auvergne
- Université de Poitiers
- Université Nice-Sophia-Antipolis
- Université de Rennes 1
- Université de Toulon
- CIRAD
- INSERM
- Institut de recherche pour le développement (IRD)
- Université d'Angers


## Overview

A detailed analysis of the contributed data provides the following overview:

### Breakdown by publisher

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Fees paid per publisher (in EURO)

```{r tree_couperin_2018_11_22_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per publisher (in EURO)

```{r box_couperin_2018_11_22_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 3])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 3 articles)") + ylab("APC")
```
