---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      Couperin.org provides additional APC data for UPMC and Paris Diderot
date:       2019-05-08 09:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

The [Couperin consortium](https://couperin.org) collects data on APC expenditures from universities and other research institutions in France. 

Additional APC expenditures by the Université Pierre et Marie Curie (Paris VI) and the Université Paris Diderot (Paris VII) have now been made available to OpenAPC.

Contact Persons for Couperin are [Valerie Larroque](mailto:valerie.larroque@couperin.org) and [Sandrine Malotaux](mailto:sandrine.malotaux@inp-toulouse.fr).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc_new <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/couperin/paris-diderot/OpenAPC_ParisDiderot_donn%C3%A9es_2017_enriched.csv"))
my.apc_new <- my.apc_new[18:35,]
my.apc_new <- droplevels(my.apc_new)
my.apc_new_2 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/couperin/upmc/OpenAPC_donn%C3%A9es_2017_upmc_enriched.csv"))
my.apc_new_2 <- my.apc_new_2[71:78,]
my.apc_new_2 <- droplevels(my.apc_new_2)
my.apc <- rbind(my.apc_new, my.apc_new_2)

```

The new data provided by Couperin covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles published in 2017. Total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€.


## Overview

A detailed analysis of the contributed data sets provides the following overview:

### Breakdown by publisher

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Fees paid per publisher (in EURO)

```{r tree_couperin_2019_05_08_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per publisher (in EURO)

```{r box_couperin_2019_05_08_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 0])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher") + ylab("APC")
```
