---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      FWF reports expenditures on APCs and BPCs
date:       2020-12-17 08:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo =FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

The [FWF](https://www.fwf.ac.at/en/) (Austrian Science fund) has updated its data on both APC and BPC expenditures.

Contact person is [Katharina Rieck](https://www.fwf.ac.at/en/about-the-fwf/organisation/fwf-team/strategy-departments/strategy-policy-evaluation-analysis/vk/krieck).

## Cost Data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "FWF - Austrian Science Fund",]
my.apc <- droplevels(my.apc)
my.apc_new <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/fwf/fwf_APC_2019_enriched.csv"))
my.apc_new <- my.apc_new[my.apc_new$institution == "FWF - Austrian Science Fund",]
my.apc_new <- droplevels(my.apc_new)
```

The new data set covers publication fees for `r format(nrow(my.apc_new), big.mark =",")` articles. Total expenditure amounts to `r format(sum(my.apc_new$euro), big.mark =",")`€ and the average fee is `r format(sum(my.apc_new$euro)/nrow(my.apc_new), big.mark =",")`€. In 2014, the FWF introduced price caps for gold OA (EUR 2500) and for hybrid OA (EUR 1500). Whenever costs exceed those caps, FWF funded authors can use other sources to cover the additional costs. In order to avoid distortions regarding mean values in the OpenAPC data set the FWF set does not include articles where these caps apply and where the additional costs were paid by other sources.

In addition, the FWF also reported cost data on BPC expenditures for the first time. These records are not listed here, but they can be inspected in the according [BPC treemap section](https://treemaps.openapc.net/apcdata/bpc/#institution/).

The following table shows the APC payments the FWF has made to publishers in 2019 (including taxes and discounts).

```{r}
d_frame = data.frame(table(my.apc_new$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_new$publisher <- factor(my.apc_new$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_new$euro, my.apc_new$publisher, length),
             tapply(my.apc_new$euro, my.apc_new$publisher, sum),
             tapply(my.apc_new$euro, my.apc_new$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

With the recent contributions included, the overall APC data for the FWF now looks as follows: 

### Fees paid per publisher (in EURO)

```{r tree_fwf_2020_12_17_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_fwf_2020_12_17_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_fwf_2020_12_17_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 100])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 100 articles)") + ylab("APC")
```
