---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      New articles ingested from OpenAPC Sweden
date:       2020-07-10 09:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 999, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

Our partner project [OpenAPC Sweden](https://github.com/Kungbib/openapc-se) collects APC data from institutions in Sweden. 

Having agreed on a biannual ingestion interval, articles added to openapc-se since our [last exchange](https://openapc.github.io/general/openapc/2020/01/14/openapc-se/) have now been added to OpenAPC as well.


## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/openapc-se/apc_se_enriched.csv")
my.apc <- my.apc[!(my.apc$institution == ""),]
my.apc <- droplevels(my.apc)

```

The ingested data covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles published by Swedish institutions (This includes articles already imported before). Total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€.

Note that OpenAPC did neither include articles already present in its [transformative agreements collection](https://github.com/OpenAPC/openapc-de/tree/master/data/transformative agreements) nor articles with a cost of 0€, so the net intake is lower than what might be expected.

The following table and plots show a breakdown of the payments.

### Overview

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Fees paid per publisher (in EURO)

```{r tree_openapc_se_2020_07_10_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_openapc_se_2020_07_10_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_openapc_se_2020_07_10_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 50])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 50 articles)") + ylab("APC")
```
