---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      Couperin.org provides additional APC data for 6 institutions
date:       2021-03-30 13:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

The [Couperin consortium](https://couperin.org) collects data on APC expenditures from universities and other research institutions in France. 

APC expenditures for 6 different institutions have now been made available to OpenAPC, with 4 of them reporting for the first time.

Contact Persons for Couperin are [Valerie Larroque](mailto:valerie.larroque@couperin.org) and [Sandrine Malotaux](mailto:sandrine.malotaux@inp-toulouse.fr).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc_1 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/couperin/ansm/OpenAPC_donn%C3%A9es_ANSM_2017-20_enriched.csv"))
my.apc_2 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/couperin/evry/OpenAPC_donn%C3%A9es_Evry_2018-20_enriched.csv"))
my.apc_3 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/couperin/ill/OpenAPC_donn%C3%A9es_ILL_2017-20_enriched.csv"))
my.apc_4 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/couperin/isara/OpenAPC_donn%C3%A9es_ISARA_2017-19_enriched.csv"))
my.apc_5 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/couperin/upem/OpenAPC_donn%C3%A9es_UPEM_2018-19_enriched.csv"))
my.apc_6 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/couperin/rennes1/OpenAPC_donn%C3%A9es_2018-2019_Rennes1_enriched.csv"))

my.apc <- rbind(my.apc_1, my.apc_2, my.apc_3, my.apc_4, my.apc_5, my.apc_6)
my.apc <- my.apc[my.apc$institution != "",]
my.apc <- droplevels(my.apc)
```

The new data set provided by Couperin covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles published between 2017 and 2020. Total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€.

The data originates from the following institutions:

- Université Evry Val-d'Essonne
- Université de Rennes 1
- Université Paris-Est Marne-la-Vallée (new)
- Institut Laue-Langevin (new)
- ISARA (new)
- ANSM (new)


## Overview

A detailed analysis of the contributed data sets provides the following overview:

### Breakdown by publisher

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Fees paid per publisher (in EURO)

```{r tree_couperin_2021_03_30_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per publisher (in EURO)

```{r box_couperin_2021_03_30_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 3])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 3 articles)") + ylab("APC")
```
