---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      University of Bonn joins OpenAPC
date:       2021-02-26 10:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

We welcome the [University of Bonn](https://www.uni-bonn.de/the-university?set_language=en) as new contributing institution to OpenAPC!

The [Bonn University and State Library](https://www.ulb.uni-bonn.de/en?set_language=en) manages services related to [Open Access](https://www.open-access.uni-bonn.de) and has provided a data set on articles published under the [Wiley DEAL](https://www.projekt-deal.de/wiley-contract/) to OpenAPC.

Contact Person is [Dr. Daniel Rudolf](mailto:openaccess@ulb.uni-bonn.de).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "Bonn U",]
my.apc <- droplevels(my.apc)
my.apc_hyb <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/unibonn/OpenAPC_DEAL_Wiley_Bonn_2019_hybrid_opt_in_enriched.csv"))
my.apc_hyb <- droplevels(my.apc_hyb)
my.apc_opt_out <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/unibonn/OpenAPC_DEAL_Wiley_Bonn_2019_hybrid_opt_out_enriched.csv"))
my.apc_opt_out <- droplevels(my.apc_opt_out)

```

The initial data set provided by the ULB consists of 3 parts: `r format(nrow(my.apc), big.mark =",")` Gold OA articles, `r format(nrow(my.apc_hyb), big.mark =",")` hybrid articles and `r format(nrow(my.apc_opt_out), big.mark =",")` articles where authors chose to opt out from Open Access. The following tables provide an overview, please note that the euro amounts for hybrid and opt out do not represent APCs, but calculated APC cost equivalents.

### Gold OA

```{r}
d_frame = data.frame(table(my.apc$journal_full_title,  dnn="Journal"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Journal)), ]                                           
                                    
my.apc$journal_full_title <- factor(my.apc$journal_full_title, levels =  d_frame$Journal)

df.summary <-cbind(tapply(my.apc$euro, my.apc$journal_full_title, length),
             tapply(my.apc$euro, my.apc$journal_full_title, sum),
             tapply(my.apc$euro, my.apc$journal_full_title, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Hybrid OA

```{r}
d_frame = data.frame(table(my.apc_hyb$journal_full_title,  dnn="Journal"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Journal)), ]                                           
                                    
my.apc_hyb$journal_full_title <- factor(my.apc_hyb$journal_full_title, levels =  d_frame$Journal)

df.summary <-cbind(tapply(my.apc_hyb$euro, my.apc_hyb$journal_full_title, length),
             tapply(my.apc_hyb$euro, my.apc_hyb$journal_full_title, sum),
             tapply(my.apc_hyb$euro, my.apc_hyb$journal_full_title, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Opt-Out from OA

```{r}
d_frame = data.frame(table(my.apc_opt_out$journal_full_title,  dnn="Journal"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Journal)), ]                                           
                                    
my.apc_opt_out$journal_full_title <- factor(my.apc_opt_out$journal_full_title, levels =  d_frame$Journal)

df.summary <-cbind(tapply(my.apc_opt_out$euro, my.apc_opt_out$journal_full_title, length),
             tapply(my.apc_opt_out$euro, my.apc_opt_out$journal_full_title, sum),
             tapply(my.apc_opt_out$euro, my.apc_opt_out$journal_full_title, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```
