---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      Couperin.org provides additional APC data for 19 institutions
date:       2021-11-02 08:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

The [Couperin consortium](https://couperin.org) collects data on APC expenditures from universities and other research institutions in France. 

APC expenditures for 19 different institutions have now been made available to OpenAPC, with 10 of them reporting for the first time.

Contact Persons for Couperin are [Valerie Larroque](mailto:valerie.larroque@couperin.org) and [Sandrine Malotaux](mailto:sandrine.malotaux@inp-toulouse.fr).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[139128:139937,]

my.apc$publisher <- gsub("American Society for Biochemistry & Molecular Biology \\(ASBMB\\)", "ASBMB", my.apc$publisher)
my.apc$publisher <- gsub("Institute of Electrical & Electronics Engineers \\(IEEE\\)", "IEEE", my.apc$publisher)
my.apc$publisher <- gsub("American Association for the Advancement of Science \\(AAAS\\)", "AAAS", my.apc$publisher)
my.apc <- my.apc[my.apc$institution != "",]
my.apc <- droplevels(my.apc)

```

The new data set provided by Couperin covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles published mostly between 2018 and 2020. Total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€.

The data originates from the following institutions:

- AgroParisTech (**new**)
- Aix-Marseille Université
- Université d'Avignon et des Pays de Vaucluse
- Université de Bordeaux
- Université de Bourgogne
- ENGEES (**new**)
- ENSTA Bretagne (**new**)
- ESPCI Paris
- Université de Franche-Comté
- Université de Haute-Alsace (**new**)
- IFREMER (**new**)
- IFSTTAR
- Université du Havre (**new**)
- Université Paris 1 Panthéon-Sorbonne (**new**)
- Université Paris Nanterre (**new**)
- Université de Perpignan - Via Domitia  (**new**)
- Sciences Po Paris (**new**)
- Sorbonne Université
- Université de Toulon

## Overview

A detailed analysis of the contributed data sets provides the following overview:

### Breakdown by publisher

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Fees paid per publisher (in EURO)

```{r tree_couperin_2021_11_02_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per publisher (in EURO)

```{r box_couperin_2021_11_02_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 3])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 3 articles)") + ylab("APC")
```
