---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      TU Berlin reports 2018 to 2020 BPC expenditures
date:       2021-03-16 08:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

The [Technische Universität Berlin](https://www.tu-berlin.de/menue/home/parameter/en/) has provided BPC expenditures for the 2018 to 2020 period.

The [TU Berlin University Library](http://www.ub.tu-berlin.de/en/home/) is in charge of the University's [Open Access Publishing Fund](http://www.ub.tu-berlin.de/en/publishing/open-access/financing-for-publications/), which also supports publishing of OA monographs.

Contact person is [Michaela Voigt](mailto:openaccess@ub.tu-berlin.de).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_bpc <- function(path = NULL, dir = "tmp", file = "bpc.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/bpc.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.bpc <- download_bpc()
my.bpc <- my.bpc[my.bpc$institution == "TU Berlin",]
my.bpc <- droplevels(my.bpc)
```

The new data set covers publication fees for `r format(nrow(my.bpc), big.mark =",")` books. Total expenditure amounts to `r sum(my.bpc$euro)`€ and the average fee is `r sum(my.bpc$euro)/nrow(my.bpc)`€.

The following tables and plots provide an overview of the payments the TU Library has made to book publishers from 2018 to 2020.

```{r}
d_frame = data.frame(table(my.bpc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.bpc$publisher <- factor(my.bpc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.bpc$euro, my.bpc$publisher, length),
             tapply(my.bpc$euro, my.bpc$publisher, sum),
             tapply(my.bpc$euro, my.bpc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Fees paid per publisher (in EURO)

```{r tree_tuberlin_2021_03_16_bpc_full}
tt <- aggregate(my.bpc$euro, by = list(my.bpc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_tuberlin_2021_03_16_bpc_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.bpc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_tuberlin_2021_03_16_bpc_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.bpc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 0])
my.bpc_reduced = my.bpc[my.bpc$publisher %in% publishers,]

  
q <- ggplot(my.bpc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher") + ylab("BPC")
```
