---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      University of Magdeburg joins OpenAPC
date:       2021-10-29 09:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

We welcome the [Otto von Guericke University Magdeburg](https://www.ovgu.de/) (OvGU) as new contributor to OpenAPC!

The [OvGU Library](https://www.ub.ovgu.de/ub/en/) operates an [Open Access publishing fund](https://www.ub.ovgu.de/en/Publication+_+Open+Access/Open+Access/Publication+Fund+for+Articles.html) which received supported under the [DFG's Open Access Publishing Programme](https://www.dfg.de/en/research_funding/programmes/infrastructure/lis/open_access/infrastructure_funding/index.html#4) until 2020.

Contact Person is [Stefanie Kutz](mailto:stefanie.kutz@ovgu.de).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "Magdeburg U",]
my.apc$publisher <- gsub("Institute of Electrical & Electronics Engineers \\(IEEE\\)", "IEEE", my.apc$publisher)
my.apc$publisher <- gsub("Association for Research in Vision and Ophthalmology \\(ARVO\\)", "ARVO", my.apc$publisher)
my.apc$publisher <- gsub("American Association for the Advancement of Science \\(AAAS\\)", "AAAS", my.apc$publisher)

my.apc <- droplevels(my.apc)

```

The initial data set covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles published in 2020. Total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€.

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

## Overview

A detailed analysis of the contributed data provides the following overview:

### Fees paid per publisher (in EURO)

```{r tree_ovgu_2021_10_29_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```


###  Average costs per publisher (in EURO)

```{r box_ovgu_2021_10_29_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 0])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher") + ylab("APC")
```
