---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      PHLU and HSLU report their 2021 APC expenditures
date:       2022-01-11 09:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

The [University of Teacher Education Lucerne](https://www.phlu.ch/) (PHLU - Pädagogische Hochschule Luzern) and the [Lucerne University of Applied Sciences and Arts](https://www.hslu.ch/en/) (Hochschule Luzern, HSLU) have updated their APC expenditures, providing data for the 2021 period.

Contact Person for all Lucerne institutions (HSLU, PHLU, Lucerne University) is [Simone Rosenkranz](mailto:Simone.Rosenkranz@zhbluzern.ch).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc_1 <- my.apc[my.apc$institution == "Pädagogische Hochschule Luzern" & my.apc$period == 2021,]
my.apc_1 <- droplevels(my.apc_1)

my.apc_2 <- my.apc[my.apc$institution == "Hochschule Luzern" & my.apc$period == 2021,]
my.apc_2 <- droplevels(my.apc_2)

```

### PHLU

The new data set for the PHLU covers publication fees for 2 articles published in 2021:

```{r}
d_frame = data.frame(table(my.apc_1$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_1$publisher <- factor(my.apc_1$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_1$euro, my.apc_1$publisher, length),
             tapply(my.apc_1$euro, my.apc_1$publisher, sum),
             tapply(my.apc_1$euro, my.apc_1$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### University of Lucerne

The data set for the University of Lucerne covers fees for 7 articles:

```{r}
d_frame = data.frame(table(my.apc_2$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_2$publisher <- factor(my.apc_2$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_2$euro, my.apc_2$publisher, length),
             tapply(my.apc_2$euro, my.apc_2$publisher, sum),
             tapply(my.apc_2$euro, my.apc_2$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```
