---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      Lib4RI reports 2017 and 2018 APC expenditures
date:       2022-02-15 10:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

[Lib4RI](https://www.lib4ri.ch/) (Library for the Research Institutes within the ETH Domain) has updated its APC expenditures, the latest contributions provide data for the 2017 and 2018 period.

Lib4RI provides APC data for four institutes: [Eawag](https://www.eawag.ch/en/) (Swiss Federal Institute of Aquatic Science and Technology), [Empa](https://www.empa.ch/) (Swiss Federal Laboratories for Materials Science and Technology), [PSI](https://www.psi.ch/en) (Paul Scherrer Institute) and [WSL](https://www.wsl.ch/en/index.html) (Swiss Federal Institute for Forest, Snow and Landscape Research).

Contact persons are [Jochen Bihn and Sarah Last](mailto:openaccess@lib4ri.ch).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution %in% c("Empa - Swiss Federal Laboratories for Materials Science and Technology", "Eawag - Swiss Federal Institute of Aquatic Science and Technology", "WSL - Swiss Federal Institute for Forest, Snow and Landscape Research", "PSI - Paul Scherrer Institute"),]
my.apc <- my.apc[my.apc$period %in% c(2017, 2018),]
my.apc$publisher <- gsub("American Association for the Advancement of Science \\(AAAS\\)", "AAAS", my.apc$publisher)
my.apc$publisher <- gsub("Institute of Electrical & Electronics Engineers \\(IEEE\\)", "IEEE", my.apc$publisher)
my.apc <- droplevels(my.apc)
my.apc_empa <- my.apc[my.apc$institution == "Empa - Swiss Federal Laboratories for Materials Science and Technology",]
my.apc_empa <- droplevels(my.apc_empa)
my.apc_eawag <- my.apc[my.apc$institution == "Eawag - Swiss Federal Institute of Aquatic Science and Technology",]
my.apc_eawag <- droplevels(my.apc_eawag)
```

The new data set covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles published at Empa and Eawag in 2017 and 2018. Total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€. The following tables and plots provide more details.

### Empa - Swiss Federal Laboratories for Materials Science and Technology

```{r}
d_frame = data.frame(table(my.apc_empa$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_empa$publisher <- factor(my.apc_empa$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_empa$euro, my.apc_empa$publisher, length),
             tapply(my.apc_empa$euro, my.apc_empa$publisher, sum),
             tapply(my.apc_empa$euro, my.apc_empa$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

#### Fees paid per publisher (in EURO)

```{r tree_lib4ri_empa_2022_02_15_full}
tt <- aggregate(my.apc_empa$euro, by = list(my.apc_empa$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```


####  Average costs per publisher (in EURO)

```{r box_lib4ri_empa_2022_02_15_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc_empa$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 0])
my.apc_empa_reduced = my.apc_empa[my.apc_empa$publisher %in% publishers,]

  
q <- ggplot(my.apc_empa_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher") + ylab("APC")
```

### Eawag - Swiss Federal Institute of Aquatic Science and Technology

```{r}
d_frame = data.frame(table(my.apc_eawag$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_eawag$publisher <- factor(my.apc_eawag$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_eawag$euro, my.apc_eawag$publisher, length),
             tapply(my.apc_eawag$euro, my.apc_eawag$publisher, sum),
             tapply(my.apc_eawag$euro, my.apc_eawag$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

#### Fees paid per publisher (in EURO)

```{r tree_lib4ri_eawag_2022_02_15_full}
tt <- aggregate(my.apc_eawag$euro, by = list(my.apc_eawag$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```


####  Average costs per publisher (in EURO)

```{r box_lib4ri_eawag_2022_02_15_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc_eawag$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 0])
my.apc_eawag_reduced = my.apc_eawag[my.apc_eawag$publisher %in% publishers,]

  
q <- ggplot(my.apc_eawag_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher") + ylab("APC")
```
