---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      Freie Universität Berlin reports its 2021 APC and BPC expenditures
date:       2022-02-09 11:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```
The [Freie Universität Berlin](http://www.fu-berlin.de/en) has updated both its APC and BPC expenditures, providing cost data for the 2021 period.

The [University Library of Freie Universität Berlin](http://www.ub.fu-berlin.de/en/) is in charge of the University's [Open Access Publication Fund](http://www.fu-berlin.de/en/sites/open_access/finanzierung/publikationsfonds/index.html), which received support by the DFG under its [Open-Access Publishing Programme](https://www.dfg.de/en/research_funding/programmes/infrastructure/lis/open_access/infrastructure_funding/index.html#4) until 2019.

Contact person is [Birgit Schlegel](mailto:birgit.schlegel@fu-berlin.de).

## Cost data (articles)

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "FU Berlin",]
my.apc <- droplevels(my.apc)
my.apc_new <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/fuberlin/APC_FU_Berlin_2021_enriched.csv"))
my.apc_new <- my.apc_new[my.apc_new$institution == "FU Berlin",]
my.apc_new <- droplevels(my.apc_new)
```

The new APC data set covers publication fees for `r format(nrow(my.apc_new), big.mark =",")` articles, total expenditure amounts to `r sum(my.apc_new$euro)`€ and the average fee is `r sum(my.apc_new$euro)/nrow(my.apc_new)`€.

```{r}
d_frame = data.frame(table(my.apc_new$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_new$publisher <- factor(my.apc_new$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_new$euro, my.apc_new$publisher, length),
             tapply(my.apc_new$euro, my.apc_new$publisher, sum),
             tapply(my.apc_new$euro, my.apc_new$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

## Overview

With the recent contribution included, the overall APC data for the FU Berlin now looks as follows:

### Fees paid per publisher (in EURO)

```{r tree_fuberlin_2022_02_09_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_fuberlin_2022_02_09_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_fuberlin_2022_02_09_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 5])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 5 articles)") + ylab("APC")
```

## Cost data (books)

```{r, cache.lazy = TRUE}
#' Download BPC spreadsheet from github which requires to Curl installed

download_bpc <- function(path = NULL, dir = "tmp", file = "bpc.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/bpc.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.bpc <- download_bpc()
my.bpc <- my.bpc[my.bpc$institution == "FU Berlin",]
my.bpc <- droplevels(my.bpc)
my.bpc_new <- download_bpc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/fuberlin/BPC_FU_Berlin_2021_enriched.csv"))
my.bpc_new <- my.bpc_new[my.bpc_new$institution == "FU Berlin",]
my.bpc_new <- droplevels(my.bpc_new)
```

The new BPC data set covers publication fees for `r format(nrow(my.bpc_new), big.mark =",")` books. Total expenditure amounts to `r sum(my.bpc_new$euro)`€ and the average fee is `r sum(my.bpc_new$euro)/nrow(my.bpc_new)`€.

The following tables provides an overview of the reported BPC payments.

```{r}
d_frame = data.frame(table(my.bpc_new$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.bpc_new$publisher <- factor(my.bpc_new$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.bpc_new$euro, my.bpc_new$publisher, length),
             tapply(my.bpc_new$euro, my.bpc_new$publisher, sum),
             tapply(my.bpc_new$euro, my.bpc_new$publisher, mean))

colnames(df.summary) <- c("Books", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

## Overview

With the recent contribution included, the overall BPC data for the FU Berlin now looks as follows:

### Fees paid per publisher (in EURO)

```{r tree_fuberlin_2022_02_09_bpc_full}
tt <- aggregate(my.bpc$euro, by = list(my.bpc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_fuberlin_2022_02_09_bpc_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.bpc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_fuberlin_2022_02_09_bpc_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.bpc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 0])
my.bpc_reduced = my.bpc[my.bpc$publisher %in% publishers,]

  
q <- ggplot(my.bpc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher") + ylab("BPC")
```
