---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      University of Applied Sciences Würzburg-Schweinfurt joins OpenAPC
date:       2022-02-16 12:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

We welcome the [University of Applied Sciences Würzburg-Schweinfurt](https://www.fhws.de/en/) (FHWS) as new contributing institution to OpenAPC!

The [FHWS Library](https://bibliothek.fhws.de/en/) manages services related to Open Access and has provided a data set on articles published under the [DEAL agreements](https://www.projekt-deal.de) with Wiley and Springer Nature to OpenAPC.

Contact Person is [Lukas Burkhardt](mailto:lukas.burkhardt@fhws.de).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc_sn <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/fhws/FHWS_DEAL2020_Springer_enriched.csv"))
my.apc_w <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/fhws/FHWS_DEAL2020_Wiley_enriched.csv"))
my.apc <- rbind(my.apc_w, my.apc_sn)
my.apc<- droplevels(my.apc)

```

The initial data set provided by the FHWS consists of `r format(nrow(my.apc), big.mark =",")` hybrid articles published under the DEAL agreements in 2020. The following table provides an overview, please note that the euro amounts do not represent real APCs, but calculated APC cost equivalents.

### Cost data

```{r}
d_frame = data.frame(table(my.apc$journal_full_title,  dnn="Journal"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Journal)), ]                                           
                                    
my.apc$journal_full_title <- factor(my.apc$journal_full_title, levels =  d_frame$Journal)

df.summary <-cbind(tapply(my.apc$euro, my.apc$journal_full_title, length),
             tapply(my.apc$euro, my.apc$journal_full_title, sum),
             tapply(my.apc$euro, my.apc$journal_full_title, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```
