---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      University of Tübingen reports its 2020 APC expenditures
date:       2022-02-24 14:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

The [Eberhard Karls Universität Tübingen](https://uni-tuebingen.de/en/) has updated its APC expenditures, the latest contribution provides data for the 2020 period.

[Tübingen University Library](https://uni-tuebingen.de/en/facilities/university-library/) is in charge of the [University's Open Access Publishing Fund](https://uni-tuebingen.de/en/facilities/university-library/publishing-research/publishing/open-access-publication-fund/), which received support under the [DFG's Open Access Publishing Programme](https://www.dfg.de/en/research_funding/programmes/infrastructure/lis/open_access/infrastructure_funding/index.html#4) until 2019.

Contact person is [Ute Grimmel-Holzwarth](mailto:openaccess@ub.uni-tuebingen.de).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "Tuebingen U",]
my.apc$publisher <- gsub("Association for Research in Vision and Ophthalmology \\(ARVO\\)", "ARVO", my.apc$publisher)
my.apc <- droplevels(my.apc)
my.apc_new <- my.apc[my.apc$period == 2020 ,]
my.apc_new <- droplevels(my.apc_new)
```

The new data set covers publication fees for `r format(nrow(my.apc_new), big.mark =",")` articles, total expenditure amounts to `r sum(my.apc_new$euro)`€ and the average fee is `r sum(my.apc_new$euro)/nrow(my.apc_new)`€.

The following table shows the payments Tübingen University Library has made to publishers in 2020.

```{r}
d_frame = data.frame(table(my.apc_new$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_new$publisher <- factor(my.apc_new$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_new$euro, my.apc_new$publisher, length),
             tapply(my.apc_new$euro, my.apc_new$publisher, sum),
             tapply(my.apc_new$euro, my.apc_new$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

## Overview

With the recent contribution included, the overall APC data for Tübingen now looks as follows:

### Fees paid per publisher (in EURO)

```{r tree_tuebingen_2022_02_24_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_tuebingen_2022_02_24_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_tuebingen_2022_02_24_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 10])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 10 articles)") + ylab("APC")
```
