---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      SNSF reports 2022 APC expenditures
date:       2023-02-07 12:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 999, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

The [Swiss National Science Foundation (SNSF)](http://www.snf.ch/en/Pages/default.aspx) has provided its APC data for the 2022 period. 

Within the framework of the SNSF's OA policy, grantees are required to publish the results of their research in the form of [Open Access publications](http://www.snf.ch/en/theSNSF/research-policies/open-access/Pages/default.aspx). APC data on those publications is kindly made available to OpenAPC.

Contact Person for the SNSF is [Julius Mattern](mailto:julius.mattern@snf.ch).


## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "Swiss National Science Foundation (SNSF)",]
my.apc$publisher <- gsub("American Association for the Advancement of Science \\(AAAS\\)", "AAAS", my.apc$publisher)
my.apc$publisher <- gsub("Association for Research in Vision and Ophthalmology \\(ARVO\\)", "ARVO", my.apc$publisher)
my.apc <- droplevels(my.apc)

my.apc_new <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/snsf/snsf_openapc_update_20230202_enriched.csv"))
my.apc_new <- my.apc_new[my.apc_new$institution == "Swiss National Science Foundation (SNSF)",]
my.apc_new <- droplevels(my.apc_new)

my.apc_2022 <- my.apc[my.apc$period == 2022,]
my.apc_2022 <- droplevels(my.apc_2022)

```

The new data set provided by the SNSF covers publication fees for `r format(nrow(my.apc_new), big.mark =",")` articles.

In total, the SNSF paid for `r format(nrow(my.apc_2022), big.mark =",")` articles in 2022, with an aggreagted expenditure of `r sum(my.apc_2022$euro)`€ and an average fee of `r sum(my.apc_2022$euro)/nrow(my.apc_2022)`€.


The following table provides an overview of all 2022 data:

```{r}
d_frame = data.frame(table(my.apc_2022$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_2022$publisher <- factor(my.apc_2022$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_2022$euro, my.apc_2022$publisher, length),
             tapply(my.apc_2022$euro, my.apc_2022$publisher, sum),
             tapply(my.apc_2022$euro, my.apc_2022$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

## Overview

With the recent contribution included, the overall APC data for the SNSF now looks as follows:

### Fees paid per publisher (in EURO)

```{r tree_snsf_2022_02_07_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_snsf_2022_02_07_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_snsf_2022_02_07_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 20])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 20 articles)") + ylab("APC")
```
