---
layout:     post
author:     Julia Bartlewski
title:      University of Siegen reports 2022 data
date:       2024-10-11 12:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}

knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 12,
  fig.height = 8
)
options(scipen = 999, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

The [University of Siegen](https://www.uni-siegen.de/start/index.html.en?lang=en) has updated its expenditures, the latest contribution provides data for the 2022 period on APCs, BPCs, and hybrid OA articles published under the Springer and Wiley DEAL agreements.

[Siegen University Library](https://www.ub.uni-siegen.de/index.php?id=1&L=1) is in charge of the [University's Open Access Publishing Fund](https://www.ub.uni-siegen.de/index.php?id=1510&L=1), which receives support by the DFG under its [Open Access Publication Funding Programme](https://www.dfg.de/en/research_funding/programmes/infrastructure/lis/open_access/infrastructure_funding/).

Contact person for the data set is [Lena Vinnemann](mailto:oa@ub.uni-siegen.de).

## Cost Data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "Siegen U",]
my.apc$publisher <- gsub("Institute of Electrical & Electronics Engineers \\(IEEE\\)", "IEEE", my.apc$publisher)
my.apc <- droplevels(my.apc)
my.apc_new <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv"))
my.apc_new <- my.apc_new[226930:226960,]
my.apc_new <- my.apc_new[my.apc_new$institution == "Siegen U",]
my.apc_new <- droplevels(my.apc_new)
```

The new data set covers publication fees for `r format(nrow(my.apc_new), big.mark =",")` articles. Total expenditure amounts to `r sum(my.apc_new$euro)`€ and the average fee is `r sum(my.apc_new$euro)/nrow(my.apc_new)`€. 

The following table provides an overview. Please note that neither articles published in **hybrid** journals under the DEAL agreement nor BPCs are included in this list, as they are aggregated in OpenAPC's [transformative agreements](https://github.com/OpenAPC/openapc-de/tree/master/data/transformative_agreements) and [BPC](https://github.com/OpenAPC/openapc-de/blob/master/data/bpc.csv) datasets, respectively.


```{r}
d_frame = data.frame(table(my.apc_new$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_new$publisher <- factor(my.apc_new$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_new$euro, my.apc_new$publisher, length),
             tapply(my.apc_new$euro, my.apc_new$publisher, sum),
             tapply(my.apc_new$euro, my.apc_new$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

## Overview

With the recent contribution included, the overall APC data for the University of Siegen now looks as follows: 

### Fees paid per publisher (in EURO)

```{r tree_siegen_2024_10_11_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_siegen_2024_10_11_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_siegen_2024_10_11_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 1])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 1 article)") + ylab("APC")
```
