---
layout:     post
author:     Julia Bartlewski
author_lnk: https://github.com/jbartlewski
title:      Hertie School joins OpenAPC
date:       2024-01-09 11:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

The Forschungszentrum Jülich collects publication cost data from German institutions as part of the DFG programme "[Open Access Publication Funding](https://www.fz-juelich.de/en/zb/open-science/open-access/monitoring-dfg-oa-publication-funding)".

When reporting their publication costs, the [Hertie School](https://www.hertie-school.org/en/) had agreed to share the data with OpenAPC as well. This data has now been transferred and integrated, making the university participate in OpenAPC for the first time.

The [Hertie School Library](https://www.hertie-school.org/en/library/) manages the institution's APC expenditures and operates the institutional Open Access repository.

Contact person is [Christopher Landes](mailto:landes@hertie-school.org).


## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "Hertie School",]
my.apc <- droplevels(my.apc)

```

The initial data set provided by the Hertie School, covers publication fees for `r format(nrow(my.apc), big.mark =",")` article.

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

