---
layout:     post
author:     Julia Bartlewski
author_lnk: https://github.com/jbartlewski
title:      ZB Zürich joins OpenAPC
date:       2024-08-06 10:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

We welcome the [Zentralbibliothek Zürich](https://www.zb.uzh.ch/en) as new contributing institution!

The [Open Access publication fund (Bretscher Fund)](https://www.zb.uzh.ch/en/services/forschungsforderung#Bretscher) supports and partially funds Gold OA publications on 20th-century social and intellectual history at the [Universität Zürich (UZH)](https://www.uzh.ch/cmsssl/en.html).

An initial data set on BPC expenditures for the 2023 period has been kindly made available to OpenAPC.

Contact Person is [Samuel Nussbaum](mailto:samuel.nussbaum@zb.uzh.ch).


## Cost data

```{r, cache.lazy = TRUE}
#' Download BPC spreadsheet from github which requires to Curl installed

download_bpc <- function(path = NULL, dir = "tmp", file = "bpc.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/bpc.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.bpc <- download_bpc()
my.bpc <- my.bpc[my.bpc$institution == "Zentralbibliothek Zürich",]
my.bpc <- droplevels(my.bpc)
```

The initial data set covers publication fees for `r format(nrow(my.bpc), big.mark =",")` book. 


```{r}
d_frame = data.frame(table(my.bpc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.bpc$publisher <- factor(my.bpc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.bpc$euro, my.bpc$publisher, length),
             tapply(my.bpc$euro, my.bpc$publisher, sum),
             tapply(my.bpc$euro, my.bpc$publisher, mean))

colnames(df.summary) <- c("Books", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```
