---
layout:     post
author:     Julia Bartlewski
author_lnk: https://github.com/jbartlewski
title:      Couperin.org provides additional APC data for 19 institutions
date:       2024-08-05 14:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

The [Couperin consortium](https://couperin.org) collects data on APC expenditures from universities and other research institutions in France. 

APC expenditures for 19 different institutions have now been made available to OpenAPC, with one institution being included for the first time.

Contact Persons for Couperin are [Valerie Larroque](mailto:valerie.larroque@couperin.org) and [Sandrine Malotaux](mailto:sandrine.malotaux@inp-toulouse.fr).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/v4.126.1-0-1/data/apc_de.csv"))
my.apc <- my.apc[225223:225593,]

my.apc$publisher <- gsub("American Society for Biochemistry & Molecular Biology \\(ASBMB\\)", "ASBMB", my.apc$publisher)
my.apc$publisher <- gsub("Institute of Electrical & Electronics Engineers \\(IEEE\\)", "IEEE", my.apc$publisher)
my.apc$publisher <- gsub("American Association for the Advancement of Science \\(AAAS\\)", "AAAS", my.apc$publisher)
my.apc <- my.apc[my.apc$institution != "",]
my.apc <- droplevels(my.apc)

```

The new data set provided by Couperin covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles, total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€. The data also contained 13 BPC records which are not listed here, as they are aggregated in OpenAPC's [BPC](https://github.com/OpenAPC/openapc-de/blob/master/data/bpc.csv) dataset.

The data originates from the following institutions:

- Avignon Université
- Centre Hospitalier Universitaire de Rennes
- CIRAD - Centre de coopération internationale en recherche agronomique pour le développement
- Ecole polytechnique
- ENGEES - Ecole nationale du Génie de l'Eau et de l'Environnement de Strasbourg
- ENSTA Bretagne - Ecole nationale supérieure de techniques avancées - Bretagne
- INSA Lyon - Institut National des Sciences Appliquées de Lyon
- LNE - Laboratoire National de Métrologie et d'Essais
- Université de Lille
- Université de Nîmes
- Université Panthéon-Sorbonne - Paris I
- Université de Paris Ouest Nanterre La Défense - Paris X
- Université de Reims Champagne-Ardenne
- Université de Rennes
- Université de Rennes II Haute-Bretagne
- Université de technologie de Troyes
- Université de Tours
- Université Le Havre Normandie
- IMT Mines Alès (**new**)



## Overview

A detailed analysis of the contributed data sets provides the following overview:

### Breakdown by publisher

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Fees paid per publisher (in EURO)

```{r tree_couperin_2024_08_05_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per publisher (in EURO)

```{r box_couperin_2024_08_05_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 2])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 2 articles)") + ylab("APC")
```
