---
layout:     post
author:     Julia Bartlewski
author_lnk: https://github.com/jbartlewski
title:      ZALF joins OpenAPC
date:       2025-04-17 10:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}

knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 12,
  fig.height = 8
)
options(scipen = 999, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

The Forschungszentrum Jülich collects publication cost data from German institutions as part of the DFG programme "[Open Access Publication Funding](https://www.fz-juelich.de/en/zb/open-science/open-access/monitoring-dfg-oa-publication-funding)".

When reporting their publication costs, the [Leibniz Centre for Agricultural Landscape Research (ZALF)](https://www.zalf.de/en/Pages/ZALF.aspx) had agreed to share the data with OpenAPC as well. This data has now been transferred and integrated, making the institution participate in OpenAPC for the first time.

Contact via the [ZALF library](mailto:bib@zalf.de).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "Leibniz-ZALF",]
my.apc <- droplevels(my.apc)

```

The initial data set covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles, total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€. Please note that articles published in **hybrid** journals under the DEAL agreement are not included in this list, as they are aggregated in OpenAPC's [transformative agreements](https://github.com/OpenAPC/openapc-de/tree/master/data/transformative_agreements) data set.


```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

## Overview

### Fees paid per publisher (in EURO)

```{r tree_zalf_2025_04_17_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per publisher (in EURO)

```{r box_zalf_2025_04_17_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
require(tidyverse)
my.apc <- my.apc %>%
  mutate(publisher = str_replace(publisher, ".+\\((\\w+)\\)", "\\1"))
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 0])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher") + ylab("APC")
```
