---
layout:     post
author:     Julia Bartlewski
author_lnk: https://github.com/jbartlewski
title:      Charité 2023 OAPK data integrated
date:       2025-02-05 08:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

The Forschungszentrum Jülich collects publication cost data from German institutions as part of the DFG programme "[Open Access Publication Funding](https://www.fz-juelich.de/en/zb/open-science/open-access/monitoring-dfg-oa-publication-funding)".

When reporting their publication costs, the [Charité – Universitätsmedizin Berlin](https://www.charite.de/) had agreed to share the data with OpenAPC as well. This data has now been transferred and integrated.

Contact person for the Charité data is [Dr. phil. Marcel Wrzesinski](mailto:openaccess@charite.de).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$institution == "Charité - Universitätsmedizin Berlin",]
my.apc <- droplevels(my.apc)

my.apc_new <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/refs/tags/v4.143.3-3-1/data/charite/oapk_2023_charit%C3%A9_-_universit%C3%A4tsmedizin_berlin_enriched.csv"))
my.apc_new <- my.apc_new[my.apc_new$institution == "Charité - Universitätsmedizin Berlin",]
my.apc_new <- droplevels(my.apc_new)
```

The new data set covers publication fees for `r format(nrow(my.apc_new), big.mark =",")` articles, total expenditure amounts to `r sum(my.apc_new$euro)`€ and the average fee is `r sum(my.apc_new$euro)/nrow(my.apc_new)`€. Please note that articles published in **hybrid** journals under the DEAL agreements are not included in this list, as they are aggregated in OpenAPC's [transformative agreements](https://github.com/OpenAPC/openapc-de/tree/master/data/transformative_agreements) data set. 


The following table provides an overview of the reported APCs: 


```{r}
d_frame = data.frame(table(my.apc_new$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_new$publisher <- factor(my.apc_new$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_new$euro, my.apc_new$publisher, length),
             tapply(my.apc_new$euro, my.apc_new$publisher, sum),
             tapply(my.apc_new$euro, my.apc_new$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```
### Additional Costs

```{r}
require(ggplot2)
require(tidyverse)

my.ac <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/refs/heads/master/data/apc_de_additional_costs.csv"))

my.apc_euro_only <- my.apc_new %>% mutate(apc = euro) %>% select(doi, apc)

ac_apc_join <- my.ac %>%
  inner_join(my.apc_euro_only)

apc_ac_long <- ac_apc_join %>%
  pivot_longer(!doi, names_to = "cost_type", values_to = "value", values_drop_na = TRUE)

apc_ac_grouped <- apc_ac_long %>%
  left_join(my.apc_new) %>%
  mutate(publisher = str_replace(publisher, ".+\\((\\w+)\\)", "\\1")) %>%
  mutate(cost_type = factor(cost_type), publisher = factor(publisher)) %>%
  group_by(cost_type, publisher) %>%
  summarize(value = sum(value), articles = n())
```

The new data also contained additional cost information for `r format(nrow(ac_apc_join), big.mark =",")` publications. The following plot shows the distribution between APCs and additional costs for these `r format(nrow(ac_apc_join), big.mark =",")` articles:


```{r additional_costs_charite_2025_02_05_full, echo = FALSE, message = FALSE}
p <- ggplot(data = apc_ac_grouped, mapping = aes(x = publisher, y = value, fill=cost_type)) +
  geom_col(position = position_stack(reverse = TRUE)) + 
  xlab('Publisher') + 
  ylab("Summarized Costs (€)") +
  guides(fill = guide_legend(title = "Cost Type")) + 
  scale_fill_manual(
    values = c("darkolivegreen3", "orange", "red", "magenta2", "darkslategray", "blue", "darkgreen", "yellow", "cyan"),
  #  labels = c("APC", "Colour Charges", "Cover Charge", "Other", "Page Charge", "Payment Fee", "Permission", "Reprint", "Submission Fee")
  ) + 
  theme(text = element_text(size = 16)) +
  coord_flip()
p

```


## Overview

With the recent contribution included, the overall APC data for the Charité now looks as follows:

### Fees paid per publisher (in EURO)

```{r tree_charite_2025_02_05_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_charite_2025_02_05_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_charite_2025_02_05_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
require(tidyverse)
my.apc <- my.apc %>%
  mutate(publisher = str_replace(publisher, ".+\\((\\w+)\\)", "\\1")) %>%
  mutate(publisher = str_replace(publisher, "Journal of Liberty and International Affairs, Institute for Research and European Studies - Bitola", "Bitola"))
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 5])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 5 article)") + ylab("APC")
```
