---
layout:     post
author:     Julia Bartlewski
author_lnk: https://github.com/jbartlewski
title:      Couperin.org provides additional APC data for 30 institutions
date:       2025-11-05 11:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

The [Couperin consortium](https://couperin.org) collects data on APC expenditures from universities and other research institutions in France. 

APC expenditures for 30 different institutions have now been made available to OpenAPC, with three institutions being included for the first time.

Contact person for Couperin is [Valerie Larroque](mailto:apc@couperin.org).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/refs/tags/v4.166.1-0-1/data/apc_de.csv"))
my.apc <- my.apc[254090:255054,]

my.apc$publisher <- gsub("American Society for Biochemistry & Molecular Biology \\(ASBMB\\)", "ASBMB", my.apc$publisher)
my.apc$publisher <- gsub("Institute of Electrical & Electronics Engineers \\(IEEE\\)", "IEEE", my.apc$publisher)
my.apc$publisher <- gsub("American Association for the Advancement of Science \\(AAAS\\)", "AAAS", my.apc$publisher)
my.apc <- my.apc[my.apc$institution != "",]
my.apc <- droplevels(my.apc)

```

The new data set provided by Couperin covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles, total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€. The data also contained BPC records which are not listed here. BPCs are aggregated in OpenAPC's [BPC](https://github.com/OpenAPC/openapc-de/blob/master/data/bpc.csv) data set.

The data originates from the following institutions:

- AgroParisTech
- Université d'Angers
- ANSM - Agence Nationale de Sécurité des Médicaments et des produits de santé
- CentraleSupélec
- ENS Lyon - Ecole normale supérieure de Lyon
- ENS Paris - Ecole normale supérieure de Paris
- ENSTA Bretagne - Ecole nationale supérieure de techniques avancées - Bretagne
- Université d'Evry-Val-d'Essonne
- Université de Haute-Alsace
- Toulouse INP - Institut National Polytechnique de Toulouse
- INRAE - Institut national de recherche pour l’agriculture, l’alimentation et l’environnement
- INSA Lyon - Institut National des Sciences Appliquées de Lyon
- IRSN - Institut de Radioprotection et de Sûreté Nucléaire
- ISARA - Institut Supérieur d'Agriculture et d'Agroalimentaire Rhône-Alpes
- Le Mans Université
- Université Claude Bernard - Lyon I
- Mines Paris - Ecole nationale supérieure des Mines de Paris
- Université Sorbonne Nouvelle - Paris III - USN
- Institut Pasteur
- Université de Pau et des Pays de l'Adour - UPPA
- Université de Perpignan Via Domitia
- Ecole polytechnique
- Université de La Réunion
- La Rochelle Université
- Université de Tours
- Université de Bretagne Occidentale - UBO
- Université du Littoral Côte d'Opale
- Centre Hospitalier Universitaire d'Orléans (**new**)
- EZUS - LYON (**new**)
- Université de Montpellier - Paul Valéry (**new**)


## Overview

A detailed analysis of the contributed data sets provides the following overview:

### Breakdown by publisher

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Fees paid per publisher (in EURO)

```{r tree_couperin_2025_11_05_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per publisher (in EURO)

```{r box_couperin_2025_11_05_full, echo = FALSE, message = FALSE}
require(ggplot2)
require(tidyverse)
my.apc <- my.apc %>%
  mutate(publisher = str_replace(publisher, ".+\\((\\w+)\\)", "\\1"))
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 5])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 5 article)") + ylab("APC")
```
