---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      TiHo Hannover 2023 and 2024 data integrated
date:       2026-06-03 08:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

The Forschungszentrum Jülich collects publication cost data from German institutions as part of the DFG programme "[Open Access Publication Funding](https://www.fz-juelich.de/en/zb/open-science/open-access/monitoring-dfg-oa-publication-funding)".

When reporting their publication costs, the [University of Veterinary Medicine Hannover, Foundation (TiHo)](https://www.tiho-hannover.de/en/) had agreed to share the data with OpenAPC as well. This data has now been transferred and integrated for both the 2023 and 2024 period.

Contact person is [Hans-Jürgen Osigus](mailto:open.access@tiho-hannover.de).

## Cost data

```{r, cache.lazy=TRUE, echo=FALSE}
require(ggplot2)
require(tidyverse)
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

VERSION <- "v5.3.40-38-11"

my.apc_de <- download_apc(c(paste("https://raw.githubusercontent.com/OpenAPC/openapc-de/refs/tags/",VERSION,"/data/apc_de.csv", sep="")))
my.ta <- download_apc(c(paste("https://raw.githubusercontent.com/OpenAPC/openapc-de/refs/tags/",VERSION,"/data/transformative_agreements/transformative_agreements.csv", sep="")))
my.apc_ta_joined <- bind_rows(my.apc_de, my.ta)
my.apc <- my.apc_ta_joined %>% filter(!is.na(euro)) %>% filter(institution == "TiHo Hannover")
my.apc <- droplevels(my.apc)

my.apc_new_1 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/refs/tags/v5.3.40-38-11/data/tihohannover/oapk_2023_tiho_hannover_enriched.csv"))
my.apc_new_2 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/refs/tags/v5.3.40-38-11/data/tihohannover/oapk_2024_tiho_hannover_enriched.csv"))
my.apc_new <- rbind(my.apc_new_1, my.apc_new_2)

my.apc_new <- my.apc_new %>% filter(!is.na(euro)) %>% filter(!is.na(institution))
my.apc_new_count <- format(nrow(my.apc_new), big.mark =",")

my.ta_apc_new_1 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/refs/tags/v5.3.40-38-11/data/tihohannover/oapk_2023_tiho_hannover_TA_enriched.csv"))
my.ta_apc_new_2 <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/refs/tags/v5.3.40-38-11/data/tihohannover/oapk_2024_tiho_hannover_TA_enriched.csv"))
my.ta_apc_new <- rbind(my.ta_apc_new_1, my.ta_apc_new_2)

my.ta_apc_new <- my.ta_apc_new %>% filter(!is.na(euro)) %>% filter(!is.na(institution))
my.ta_apc_new_count <- format(nrow(my.ta_apc_new), big.mark =",")

my.all_apc_new <- bind_rows(my.apc_new, my.ta_apc_new)
my.all_apc_new <- droplevels(my.all_apc_new)


```

The new data covers APCs for `r format(nrow(my.all_apc_new), big.mark =",")` articles (`r my.apc_new_count` unrelated to any agreement, `r my.ta_apc_new_count` published under an agreement like DEAL). Total APC expenditure amounts to `r sum(my.all_apc_new$euro)`€ and the average fee is `r sum(my.all_apc_new$euro)/nrow(my.all_apc_new)`€.

The following table provides an overview.

```{r}
d_frame = data.frame(table(my.apc_new$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc_new$publisher <- factor(my.apc_new$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc_new$euro, my.apc_new$publisher, length),
             tapply(my.apc_new$euro, my.apc_new$publisher, sum),
             tapply(my.apc_new$euro, my.apc_new$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```


## Overview

With the recent contribution included, the overall APC data for the TiHo now looks as follows:

### Fees paid per publisher (in EURO)

```{r tree_tiho_2026_06_03_full, echo=FALSE, message = FALSE}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_tiho_2026_06_03_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_tiho_2026_06_03_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
require(tidyverse)
my.apc <- my.apc %>%
  mutate(publisher = str_replace(publisher, ".+\\((\\w+)\\)", "\\1"))
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 5])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 5 articles)") + ylab("APC")
```
