---
layout:     post
author:     Julia Bartlewski
author_lnk: https://github.com/jbartlewski
title:      ZB Zürich reports 2025 BPC expenditures
date:       2026-07-20 09:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```
The [Zentralbibliothek Zürich](https://www.zb.uzh.ch/en) has updated its BPC expenditures, the latest contribution provides data for the 2025 period.

The [Open Access publication fund (Bretscher Fund)](https://www.zb.uzh.ch/en/services/forschungsforderung#Bretscher) supports and funds Gold OA publications on 20th-century social and intellectual history at the [Universität Zürich (UZH)](https://www.uzh.ch/cmsssl/en.html).

Contact Person is [Samuel Nussbaum](mailto:samuel.nussbaum@zb.uzh.ch).

## Cost data

```{r, cache.lazy = TRUE}
#' Download BPC spreadsheet from github which requires to Curl installed

download_bpc <- function(path = NULL, dir = "tmp", file = "bpc.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/bpc.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.bpc <- download_bpc()
my.bpc <- my.bpc[my.bpc$institution == "Zentralbibliothek Zürich",]
my.bpc <- droplevels(my.bpc)
my.bpc_new <- download_bpc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/zb_zuerich/zbzuerich_openapc_bpc_2025_enriched.csv"))
my.bpc_new <- my.bpc_new[my.bpc_new$institution == "Zentralbibliothek Zürich",]
my.bpc_new <- droplevels(my.bpc_new)
```

The new data set covers publication fees for `r format(nrow(my.bpc_new), big.mark =",")` book. 

The following table provides an overview of the reported BPC payments.

```{r}
d_frame = data.frame(table(my.bpc_new$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.bpc_new$publisher <- factor(my.bpc_new$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.bpc_new$euro, my.bpc_new$publisher, length),
             tapply(my.bpc_new$euro, my.bpc_new$publisher, sum),
             tapply(my.bpc_new$euro, my.bpc_new$publisher, mean))

colnames(df.summary) <- c("Books", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

## Overview

With the recent contribution included, the overall BPC data for the ZB Zürich now looks as follows:

### Fees paid per publisher (in EURO)

```{r tree_zbzuerich_2026_07_20_bpc_full}
tt <- aggregate(my.bpc$euro, by = list(my.bpc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_zbzuerich_2026_07_20_bpc_year_full, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.bpc, aes(factor(period), euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_zbzuerich_2026_07_20_bpc_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
d_frame = data.frame(table(my.bpc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 0])
my.bpc_reduced = my.bpc[my.bpc$publisher %in% publishers,]

  
q <- ggplot(my.bpc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher") + ylab("BPC")
```
