---
layout:     post
author:     Christoph Broschinski
author_lnk: https://github.com/cbroschinski
title:      The National Library of Sweden provides cost data for 19 institutions
date:       2026-04-17 17:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

The [National Library of Sweden](https://www.kb.se/in-english.html) collects data on APC and BPC expenditures from universities and other research institutions in Sweden. 

Publication costs for 19 different institutions have now been made available to OpenAPC.

Contact person for the National Library is [Johan Fröberg](mailto:openaccess@kb.se).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/v4.153.4-3-2/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/refs/tags/v5.3.1-0-1/data/apc_de.csv"))
my.apc <- my.apc[253676:254797,]

my.apc$publisher <- gsub("Institute of Electrical & Electronics Engineers \\(IEEE\\)", "IEEE", my.apc$publisher)
my.apc$publisher <- gsub("American Association for the Advancement of Science \\(AAAS\\)", "AAAS", my.apc$publisher)
my.apc <- my.apc[my.apc$institution != "",]
my.apc <- droplevels(my.apc)
```

The new data set provided by the National Library covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles. Total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€.

The data originates from the following institutions:

- Karolinska Institutet
- KTH Royal Institute of Technology
- Swedish Defence University (**new**)
- Swedish University of Agricultural Sciences
- University of Gävle
- Jönköping University
- Karlstad University
- Linköping University
- Linnaeus University
- Luleå University of Technology
- Lund University
- Mälardalen University
- Malmö University
- Mid Sweden University
- Örebro University
- Södertörns University
- Stockholm University
- Uppsala University
- University West

## Overview

A detailed analysis of the contributed data sets provides the following overview:

### Breakdown by publisher

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Fees paid per publisher (in EURO)

```{r tree_natlibswe_2026_04_17_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per publisher (in EURO)

```{r box_natlibswe_2026_04_17_publisher_full, echo = FALSE, message = FALSE}
require(ggplot2)
require(tidyverse)
my.apc <- my.apc %>%
mutate(publisher = str_replace(publisher, ".+\\((\\w+)\\)", "\\1"))
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 20])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 20 articles)") + ylab("APC")
```
