---
layout:     post
author:     Julia Bartlewski
author_lnk: https://github.com/jbartlewski
title:      Couperin.org provides APC data for 29 institutions
date:       2026-01-28 11:00:00
summary:    
categories: [general, openAPC]
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

The [Couperin consortium](https://couperin.org) collects data on APC expenditures from universities and other research institutions in France. 

APC expenditures for 29 different institutions have now been made available to OpenAPC, with five institutions being included for the first time.

Contact person for Couperin is [Valerie Larroque](mailto:apc@couperin.org).

## Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc(c("https://raw.githubusercontent.com/OpenAPC/openapc-de/refs/tags/v4.167.1-0-1/data/apc_de.csv"))
my.apc <- my.apc[259799:261097,]

my.apc$publisher <- gsub("American Society for Biochemistry & Molecular Biology \\(ASBMB\\)", "ASBMB", my.apc$publisher)
my.apc$publisher <- gsub("Institute of Electrical & Electronics Engineers \\(IEEE\\)", "IEEE", my.apc$publisher)
my.apc$publisher <- gsub("American Association for the Advancement of Science \\(AAAS\\)", "AAAS", my.apc$publisher)
my.apc <- my.apc[my.apc$institution != "",]
my.apc <- droplevels(my.apc)

```

The new data set provided by Couperin covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles, total expenditure amounts to `r sum(my.apc$euro)`€ and the average fee is `r sum(my.apc$euro)/nrow(my.apc)`€. The data also contained BPC records which are not listed here. BPCs are aggregated in OpenAPC's [BPC](https://github.com/OpenAPC/openapc-de/blob/master/data/bpc.csv) data set.

The data originates from the following institutions:

- Aix-Marseille Université
- Université Clermont Auvergne
- Université de Bordeaux
- Ecole centrale de Lyon
- Centre Hospitalier Universitaire de Lille
- Université de Technologie de Compiègne
- EnvA - Ecole nationale vétérinaire d'Alfort
- Université Gustave Eiffel
- HCL - Hospices civils de Lyon
- INSERM - Institut National de la Santé et de la Recherche Médicale
- Université de Limoges
- LNE - Laboratoire National de Métrologie et d'Essais
- Université de Lorraine
- Université de Montpellier
- Nantes Université
- Université Vincennes-Saint Denis - Paris VIII
- Université Paris-Dauphine - Paris IX
- Université de Poitiers
- Sciences Po Paris - Institut d'Etudes Politiques de Paris
- Sorbonne Université
- Université Toulouse - Jean Jaurès
- Université de Bretagne Sud - UBS
- Université Paris-Est Créteil Val de Marne - Paris XII
- Université de Versailles Saint-Quentin-en-Yvelines
- Université Marie et Louis Pasteur (**new**)
- Centrale Nantes (**new**)
- ENPC - École des Ponts ParisTech (**new**)
- INSA Toulouse - Institut National des Sciences Appliquées de Toulouse (**new**)
- INSEP - Institut National du Sport, de l'Expertise et de la Performance (**new**)


## Overview

A detailed analysis of the contributed data sets provides the following overview:

### Breakdown by publisher

```{r}
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

df.summary <-cbind(tapply(my.apc$euro, my.apc$publisher, length),
             tapply(my.apc$euro, my.apc$publisher, sum),
             tapply(my.apc$euro, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```

### Fees paid per publisher (in EURO)

```{r tree_couperin_2026_01_28_full}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per publisher (in EURO)

```{r box_couperin_2026_01_28_full, echo = FALSE, message = FALSE}
require(ggplot2)
require(tidyverse)
my.apc <- my.apc %>%
  mutate(publisher = str_replace(publisher, ".+\\((\\w+)\\)", "\\1"))
d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]
publishers = as.character(d_frame$Publisher[d_frame$Freq > 10])
my.apc_reduced = my.apc[my.apc$publisher %in% publishers,]

  
q <- ggplot(my.apc_reduced, aes(publisher, euro)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18) + coord_flip()
q + xlab("Publisher (> 10 article)") + ylab("APC")
```
