---
layout: page
title: About
permalink: /about/
---

```{r, echo =FALSE}

knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 0, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

The aim of this repository is:

- to release datasets on fees paid for Open Access journal articles by Universities and Research Society Funds under an Open Database License
- to demonstrate how reporting on fee-based Open Access publishing can be made more transparent and reproducible across institutions.

## Participating German Universities

So far, the following German universities have agreed to share information on paid author processing charges (APC):

- [Bayreuth University](http://www.ub.uni-bayreuth.de/en/digitale_bibliothek/open_access/index.html)
- [Bielefeld University](http://oa.uni-bielefeld.de/publikationsfonds.html)
- [Clausthal University of Technology](http://www.ub.tu-clausthal.de/en/angebote-fuer-wissenschaftlerinnen/elektronisches-publizieren/publikationsfonds/)
- [Freie Universität Berlin](http://www.fu-berlin.de/sites/open_access/finanzierung/publikationsfonds/index.html)
- [Friedrich-Alexander-Universität Erlangen-Nürnberg](https://ub.fau.de/schreiben-publizieren/open-access/dfg-gefoerderter-publikationsfonds/)
- [Hamburg University of Technology](https://www.tub.tu-harburg.de/publizieren/openaccess/)
- [Heidelberg University](http://www.ub.uni-heidelberg.de/Englisch/service/openaccess/publikationsfonds.html)
- [Leibniz Universität Hannover](https://tib.eu/oafonds)
- [Leipzig University](https://www.ub.uni-leipzig.de/forschungsbibliothek/projekte/projekte-chronologisch/open-access-publikationsfonds/)
- [Ludwig-Maximilians-Universität München](http://www.en.ub.uni-muenchen.de/writing/open-access-publishing/funding/index.html)
- [Martin-Luther-Universität Halle-Wittenberg](http://bibliothek.uni-halle.de/dbib/openaccess/publikationsfonds/)
- [Münster University](https://www.uni-muenster.de/Publizieren/service/publikationsfonds/)
- [JGU Mainz](https://www.openaccess.uni-mainz.de/publikationsfonds-der-jgu/)
- [JLU Giessen](https://www.uni-giessen.de/ub/en/digitales-publizieren-en/openaccess-en/oajlu-en?set_language=en)
- [KIT Karlsruhe](http://www.bibliothek.kit.edu/cms/kit-publikationsfonds.php)
- [Osnabrück University](https://www.ub.uni-osnabrueck.de/publizieren_archivieren/open_access/publikationsfonds.html)
- [Ruhr Universität Bochum](http://www.ruhr-uni-bochum.de/oa/)
- [Technische Universität Berlin](http://www.ub.tu-berlin.de/publikationsfonds/)
- [Technische Universität Braunschweig](https://ub.tu-braunschweig.de/publikationsfonds/)
- [Technische Universität Chemnitz](https://www.tu-chemnitz.de/ub/publizieren/openaccess/index.html.en)
- [Technische Universität Darmstadt](https://www.ulb.tu-darmstadt.de/service/elektronisches_publizieren/oa_publikationsfond/index.en.jsp)
- [Technische Universität Dortmund](http://www.ub.tu-dortmund.de/open-access/index.html)
- [Technische Universität Dresden](http://www.slub-dresden.de/service/schreiben-publizieren/open-access-service/publikationsfonds/)
- [Technische Universität Ilmenau](https://www.tu-ilmenau.de/ub/service/open-access/oa-publikationsfonds/)
- [Technische Universität München](https://www.ub.tum.de/en/publishing-fund)
- [University of Bamberg](http://www.uni-bamberg.de/en/ub/publishing/open-access-publishing/open-access-funds/)
- [University of Bremen](http://www.suub.uni-bremen.de/home-english/refworks-and-publishing/open-access-in-bremen-2/)
- [University of Duisburg-Essen](https://www.uni-due.de/ub/en/openaccess_foerderung.shtml)
- [University of Freiburg](https://www.ub.uni-freiburg.de/unterstuetzung/elektronisch-publizieren/open-access/publikationsfonds/)
- [University of Göttingen](http://www.sub.uni-goettingen.de/en/electronic-publishing/open-access/open-access-publication-funding/)
- [University of Kassel](http://www.uni-kassel.de/go/publikationsfonds)
- [University of Konstanz](https://www.kim.uni-konstanz.de/en/services/scholarly-publishing-and-open-access/open-access-publication-funds/)
- [University of Oldenburg](http://www.bis.uni-oldenburg.de/en/teachingresearchingpublishing/publishing/openaccesspublishing/open-access-publication-fund/)
- [University of Potsdam](https://publishup.uni-potsdam.de/home/index/help/content/publication_fund)
- [University of Regensburg](http://oa.uni-regensburg.de/)
- [University of Stuttgart](https://oa.uni-stuttgart.de/publizieren/fonds/)
- [University of Trier](https://www.uni-trier.de/index.php?id=60802)
- [University of Tübingen](https://www.uni-tuebingen.de/en/facilities/university-library/researching-publishing/open-access-publikationsfonds.html)
- [University of Veterinary Medicine Hannover, Foundation (TiHo)](http://www.tiho-hannover.de/de/kliniken-institute/bibliothek/open-access/publikationsfonds-an-der-tiho/)
- [University of Würzburg](http://www.bibliothek.uni-wuerzburg.de/en/service0/electronic_publishing/open_access/open_access_journals/)
- [Ulm University](https://www.uni-ulm.de/index.php?id=57202)

## Participating Research Society Funds in Germany

Dataset on funds that are supported by research societies under its Open-Access Publishing Programme.

Participating Research Organizations:

- [Max Planck Digital Library](http://www.mpdl.mpg.de/21-specials/50-open-access-publishing.html)

The data content covers APCs as paid for by our central budget for the Max Planck Society (MPS). APCs funded locally by Max Planck Institutes are not part of this data set. The MPS has a limited input tax reduction. The refund of input VAT for APC is 20%. Until the end of 2007 the MPS was VAT exempt.

- [Fraunhofer Publishing Fund](https://www.openaccess.fraunhofer.de/en/open-access-strategy.html)
- [Forschungszentrum Jülich](http://www.fz-juelich.de/portal/DE/Home/home_node.html)
- [GIGA German Institute of Global and Area Studies](https://www.giga-hamburg.de/en/giga-open-access-guidelines)
- [Helmholtz-Zentrum Dresden-Rossendorf](http://www.hzdr.de/db/Cms?pNid=73)
- [Helmholtz-Zentrum für Umweltforschung - UFZ](https://www.ufz.de/index.php?de=33573)
- [IGB - Leibniz-Institute of Freshwater Ecology and Inland Fisheries](http://www.igb-berlin.de/bibliothek)
- [INM - Leibniz Institute for New Materials](http://bibliothek.inm-gmbh.de/publizieren/publikationsgebuhren/)
- [IPN - Leibniz Institute for Science and Mathematics Education](http://www.ipn.uni-kiel.de/en/the-ipn/library/open-access)
- [Leibniz Association's Open Access Publishing Fund](http://www.leibniz-gemeinschaft.de/en/infrastructures/open-access/open-access-publishing-fund/)
- [Library Wissenschaftspark Albert Einstein](http://bib.telegrafenberg.de/en/library-wissenschaftspark-albert-einstein/)
- [Max Delbrück Center for Molecular Medicine (MDC)](https://www.mdc-berlin.de/1161876/de/about_the_mdc/structure/administration/library)
- [Technische Informationsbibliothek (TIB) - German National Library of Science and Technology](https://www.tib.eu/en/service/tib-open-access-policy/)
- [WIAS - Weierstrass Institute for Applied Analysis and Stochastics](https://www.wias-berlin.de/services/library/)

## Participating Austrian Institutions

- [FWF - Austrian Science Fund](https://www.fwf.ac.at/en/research-funding/open-access-policy/)
- [Institute of Science and Technology Austria](https://ist.ac.at/open-access/open-access-policy/)
- [Technische Universität Wien](http://www.ub.tuwien.ac.at/eng/openaccess)

## Participating Swiss Institutions

- [SNSF - Swiss National Science Foundation](http://www.snf.ch/en/theSNSF/research-policies/open-access/Pages/default.aspx#OA%202020%20Policy)

## Participating Italian Institutions

- [Università degli Studi di Milano](http://www.unimi.it/ENG/)

## Institutions from Norway:

- Akershus University Hospital
- BI Norwegian Business School
- Bergen University College
- Fridtjof Nansen Institute
- GenØk - Centre for Biosafety
- Harstad University College
- Innlandet Hospital Trust
- Institute of Marine Research
- Molde University College
- NILU - Norwegian Institute for Air Research
- Nansen Environmental and Remote Sensing Center
- Nord University
- Norwegian Center for Studies on Violence and Traumatic Stress
- Norwegian Institute for Agricultural and Environmental Research
- Norwegian Institute for Nature Research
- Norwegian Institute of Public Health
- Norwegian Institute of Water Research
- Norwegian School of Sport Sciences
- Norwegian University of Life Sciences
- Norwegian University of Science and Technology
- Oslo University Hospital
- Oslo and Akershus university college
- SINTEF (Foundation for Scientific and Industrial Research)
- Sørlandet Hospital Trust
- Uni Research
- University College of Southeast Norway
- University of Agder
- University of Bergen
- University of Oslo
- University of Stavanger
- University of Tromsø - The Arctic University of Norway
- Vestfold Hospital Trust
- Vestre Viken Hospital Trust

## Participating Spanish Institutions:

- [Universitat de Barcelona](http://www.ub.edu/web/ub/en/index.html)

## Institutions from Sweden (via [Open APC Sweden](https://github.com/Kungbib/openapc-se)):

- Chalmers University of Technology
- Dalarna University College
- University of Gothenburg
- Borås University College
- University College West
- Karolinska Institutet
- KTH Royal Institute of Technology
- Linköping University
- Linnaeus University
- Luleå University of Technology
- Lund University
- Malmö University
- Örebro University
- Swedish University of Agricultural Sciences
- Stockholm University
- Umeå University
- Uppsala University

## Institutions from France

The [Couperin consortium](https://couperin.org) aggregates data on APC expenditures made by institutions in France:

- Aix-Marseille Université
- Université d'Angers
- Université de Bordeaux
- Université de Bourgogne
- Centre de coopération internationale en recherche agronomique pour le développement (CIRAD)
- Centre national de la recherche scientifique (CNRS)
- Ecole normale supérieure de Paris
- École supérieure de physique et de chimie industrielles de la Ville de Paris (ESPCI)
- Hospices Civils de Lyon
- Université Grenoble Alpes
- Institut de recherche pour le développement (IRD)
- Institut français des sciences et technologies des transports, de l'aménagement et des réseaux (IFSTTAR)
- Institut national de recherche en informatique et en automatique (INRIA)
- Institut national de la recherche agronomique (INRA)
- Institut national de recherche en sciences et technologies pour l'environnement et l'agriculture (IRSTEA)
- Institut national de la santé et de la recherche médicale (INSERM)
- Institut national polytechnique de Toulouse (INPT)
- Université d'Avignon et des Pays de Vaucluse
- Université de Caen Normandie
- Université Claude Bernard Lyon 1
- Université Clermont Auvergne
- Université de France-Comté
- Université Lille 1
- Université Lille 2
- Université de Lorraine
- Université de Nantes
- Université Nice-Sophia-Antipolis
- Université de Poitiers
- Université de Rennes 1
- Université de Strasbourg
- Université de Toulon
- Université Toulouse III
- Université Paris Descartes (Paris V)
- Université Pierre et Marie Curie (Paris VI)
- Université Paris Diderot (Paris VII)


## Participating Institutions from the United Kingdom:

- [Wellcome Trust](https://wellcome.ac.uk/funding/managing-grant/open-access-policy)
- [JISC](https://www.jisc-collections.ac.uk/Jisc-Monitor/APC-data-collection/)

Jisc Collections released data on APC payments made by UK higher education institutions (HEIs):

- Aberystwyth University
- Aston University
- Bangor University
- Brunel University
- Cardiff University
- Cranfield University
- Edinburgh Napier University
- Glasgow Caledonian University
- Goldsmiths
- Heriot-Watt University
- Imperial College London
- Institute of Cancer Research (ICR)
- Keele University
- King's College London
- Leeds Beckett University
- Liverpool John Moores University
- Liverpool School of Tropical Medicine
- London School of Economics (LSE)
- London School of Hygiene & Tropical Medicine (LSHTM)
- Lancaster University
- Manchester Metropolitan University
- Northumbria University
- Plymouth University
- Queen Mary, University of London
- Queen's University Belfast
- Royal Holloway
- St George's, University of London
- Swansea University
- The Open University
- University College London (UCL)
- University of Aberdeen
- University of Bath
- University of Birmingham
- University of Bristol
- University of Cambridge
- University of Dundee
- University of Durham
- University of East Anglia
- University of Edinburgh
- University of Exeter
- University of Glasgow
- University of Huddersfield
- University of Hull
- University of Kent
- University of Leeds
- University of Leicester
- University of Liverpool
- University of Loughborough
- University of Manchester
- University of Newcastle
- University of Nottingham
- University of Oxford
- University of Portsmouth
- University of Reading
- University of Salford
- University of Sheffield
- University of Southampton
- University of St Andrews
- University of Strathclyde
- University of Surrey
- University of Sussex
- University of the West of England
- University of Ulster
- University of Warwick
- University of York


## Participating Institutions from the Czech Republic (contributed by [CzechELib](https://www.czechelib.cz/en/)):

- [University of Chemistry and Technology, Prague](https://www.vscht.cz/?jazyk=en)

## Participating Institutions from the United States:

- [Harvard University](https://osc.hul.harvard.edu/programs/hope/)
- [Indiana University - Purdue University Indianapolis (IUPUI)](http://www.ulib.iupui.edu/digitalscholarship/openaccess/oafund)
- [University of Rhode Island](https://uri.libguides.com/oafund)
- [Virginia Polytechnic Institute and State University](http://guides.lib.vt.edu/oa)

## Participating Canadian Institutions:

- [University of Calgary](http://library.ucalgary.ca/open-access-authors-fund)

## Supranational participants

- [OpenAIRE](https://www.openaire.eu/postgrantoapilot) (FP7 Post-Grant Open Access Pilot)

## Dataset

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- droplevels(my.apc)
```
Information on both open access journal articles and open access publication of articles in toll-access journals ("hybrid") are provided.

In total,  `r format(sum(my.apc$euro), scientific=FALSE)` € for  `r nrow(my.apc)` articles were paid by the participating unviversities. Average  fee is `r format(sum(my.apc$euro)/nrow(my.apc), digits = 5)` € and the median `r median(my.apc$euro)` €.

### Open Access Journals

```{r, echo=FALSE, cache = FALSE}
my.apc <- download_apc()
my.apc <- my.apc[my.apc$is_hybrid == FALSE,]
```

At the moment, the dataset releases information on `r nrow(my.apc)` articles in open access journals which charge publication fees. Total expenditure amounts to  `r format(sum(my.apc$euro), scientific=FALSE)` €. Average  fee is `r format(sum(my.apc$euro)/nrow(my.apc), digits = 5)` € and the median `r median(my.apc$euro)` €.

View dataset on [GitHub](https://github.com/OpenAPC/openapc-de/blob/master/data/apc_de.csv).

```{r, echo=FALSE, results='asis', message = FALSE}
my.apc <- download_apc()
my.apc <- my.apc[my.apc$is_hybrid == FALSE,]

df.summary <-cbind(tapply(my.apc$euro, my.apc$institution, length),
             tapply(my.apc$euro, my.apc$institution, sum),
             tapply(my.apc$euro, my.apc$institution, mean),
             tapply(my.apc$euro, my.apc$institution, median))
colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid", "Median")

knitr::kable(as.data.frame(df.summary), format.args = list(scientific = FALSE, big.mark = ","))
```

### Hybrid articles

```{r, echo=FALSE, cache = FALSE}
my.apc <- download_apc()
my.apc <- my.apc[my.apc$is_hybrid == TRUE,]
```

In many toll-access journals some of the articles are open access after a fee has been paid. This model is often called "hybrid open access".
The dataset covers `r nrow(my.apc)` hybrid open access articles. Total expenditure amounts to  `r format(sum(my.apc$euro), scientific=FALSE)` €. Average  fee is `r format(sum(my.apc$euro)/nrow(my.apc), digits = 5)` € and the median `r median(my.apc$euro)` €.

The following institutions have contributed its expenditures for hybrid open access.

```{r, echo=FALSE, cache = FALSE}
my.apc <- download_apc()
my.apc <- my.apc[my.apc$is_hybrid == TRUE,]
my.apc <- droplevels(my.apc)

df.summary <-cbind(tapply(my.apc$euro, my.apc$institution, length),
             tapply(my.apc$euro, my.apc$institution, sum),
             tapply(my.apc$euro, my.apc$institution, mean),
             tapply(my.apc$euro, my.apc$institution, median))
colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid", "Median")

knitr::kable(as.data.frame(df.summary), format.args = list(scientific = FALSE, big.mark = ","))
```

## Use of external sources

External sources were used to compile the dataset. This allows for disambiguated information on publishers and journals in order to make cost data comparable. Shared identifiers for publications (e.g. PMID) are provided as well.

|Source     |variable  |description                     |
|:--------------|:---------|:-----------------------------------------------|
|CrossRef   |`publisher` |Title of Publisher             |
|CrossRef   |`journal_full_title` |Full Title of Journal  |
|CrossRef   |`issn` |International Standard Serial Numbers (collapsed) |
|CrossRef   |`issn_print` |ISSN print |
|CrossRef   |`issn_electronic`  |ISSN electronic        |
|CrossRef   |`license_ref`  |License of the article     |
|CrossRef   |`indexed_in_crossref`  |Is the article metadata registered with CrossRef? (logical)    |
|ISSN International Centre |`issn_l` | Linking ISSN |
|EuropePMC    |`pmid`  |PubMed ID                 |
|EuropePMC    |`pmcid` |PubMed Central ID         |
|Web of Science |`ut` |Web of Science record ID             |
|DOAJ           |`doaj` |Is the journal indexed in the DOAJ? (logical)    |

## Sample Visualisations

### Distribution over publishers by university

```{r uni_publisher, fig.width=10.5, fig.height=4.5}
require(ggplot2)
require(RColorBrewer)

#load data

my.apc <- download_apc()
#only unis
my.apc <- my.apc[!my.apc$institution %in% c("MPG", "FZJ - ZB", "GFZ-Potsdam", "INM - Leibniz-Institut für Neue Materialien", "MDC", "FWF - Austrian Science Fund", "Leibniz-Fonds"),]

## Choose only publisher with at least 5 publication (abritary)

# relevel
my.apc$publisher <- factor(my.apc$publisher, 
                           levels =  c(rownames(data.frame(rev(sort(tapply(my.apc$euro, list(my.apc$publisher), sum)))))))
## my.apc$institution <- factor(my.apc$institution, levels =  c(rownames(data.frame(rev(sort(table(my.apc$institution)))))))

d_frame = data.frame(table(my.apc$institution,  dnn="Institution"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Institution)), ]                                           
                                    
my.apc$institution <- factor(my.apc$institution, levels =  d_frame$Institution)



levels(my.apc$publisher)[6:length(levels(my.apc$publisher))] <- paste("other (n=", 
                                                                      length(unique(my.apc$publisher)) - 5, ")", sep="")

my.df <- aggregate(my.apc$euro, list(publisher =my.apc$publisher, Uni = my.apc$institution), sum)

## Plot by publisher
colour_count <- length(unique(my.df$Uni))

p <- ggplot(my.df, aes(publisher, x, fill= Uni)) + geom_bar(stat="identity")  + ylab("Fees paid (in EURO)") + coord_flip() + 
  scale_y_continuous(limits=c(0, 1250000), labels=function(x) format(x, big.mark = ".", scientific = FALSE)) + 
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Set3"))(colour_count)) +
  theme_bw() + theme(legend.text = element_text(size = 12, colour = "black")) +
  guides(fill=guide_legend(ncol=2)) 

p
```


### Comparing fees paid by university and research institution

```{r box_all, echo = FALSE}

my.apc <- download_apc()
my.apc <- droplevels(my.apc)

q <- ggplot(my.apc, aes(institution, euro)) + geom_boxplot() + geom_point(alpha = 8/10, size = 2,aes(colour =is_hybrid)) + scale_colour_manual(values = c("#000A02", "#DC4E00"))
q <- q +  ylab("Fees paid (in EURO)") + coord_flip() + theme(legend.position="top") + theme_bw()

q
```


### Average fees paid by publisher

```{r box_publisher, echo=FALSE}

my.apc <- download_apc()
my.apc <- droplevels(my.apc)

# relevel
## my.apc$publisher <- factor(my.apc$publisher, levels =  c(rownames(data.frame(rev(sort(table(my.apc$publisher)))))))

d_frame = data.frame(table(my.apc$publisher,  dnn="Publisher"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Publisher)), ]                                           
                                    
my.apc$publisher <- factor(my.apc$publisher, levels =  d_frame$Publisher)

## my.apc$institution <- factor(my.apc$institution, levels =  c(rownames(data.frame(rev(sort(table(my.apc$institution)))))))

d_frame = data.frame(table(my.apc$institution,  dnn="Institution"))                 
d_frame = d_frame[with(d_frame, order(-Freq, Institution)), ]                                           
                                    
my.apc$institution <- factor(my.apc$institution, levels =  d_frame$Institution)

levels(my.apc$publisher)[6:length(levels(my.apc$publisher))] <- paste("other (n=", 
                                                                      length(unique(my.apc$publisher)) - 5, ")", sep="")

q <- ggplot(my.apc, aes(publisher, euro)) + geom_boxplot() + geom_point(alpha = 8/10, size = 2,aes(colour =is_hybrid)) + scale_colour_manual(values = c("#000A02", "#DC4E00"))
q <- q +  ylab("Fees paid (in EURO)") + coord_flip() + theme(legend.position="top") + theme_bw()

q
```


### Average fees Max Planck Digital Library paid for Springer Open Access articles by year

```{r box_mpdl_springer, echo=FALSE}
my.apc <- download_apc()
my.apc <- droplevels(my.apc)

mpg <- my.apc[my.apc$institution == "MPG" & my.apc$publisher == "Springer Science + Business Media",]
q <- ggplot(mpg, aes(factor(period), euro)) + geom_boxplot() + geom_point(alpha = 2/10, size = 2)
q <- q +  ylab("Fees paid (in EURO)") + xlab("Period") + theme(legend.position="top") + theme_bw()

q
```


For more examples see also [http://openapc.github.io/openapc-de/](http://openapc.github.io/openapc-de/)

## How to contribute?

In collaboration with the [DINI working group Electronic Publishing](http://dini.de/ag/e-pub1/), a [wiki page](https://github.com/OpenAPC/openapc-de/wiki/Handreichung-Dateneingabe)(in German) explains all the steps required. Meeting and telephone conferences are documented as well:

* [Virtual Meeting 19 August](https://github.com/OpenAPC/openapc-de/wiki/Protokoll-Kick-Off-19.-August)
* [Virtual Meeting 11 + 12 February 2015](https://github.com/OpenAPC/openapc-de/wiki/Ergebnisprotokoll-11-bzw.-12.-Februar-2015)

## License

The datasets are made available under the Open Database License: http://opendatacommons.org/licenses/odbl/1.0/. Any rights in individual contents of the database are licensed under the Database Contents License: http://opendatacommons.org/licenses/dbcl/1.0/ 

This work is licensed under the Creative Commons Attribution 4.0 Unported License.

## How to cite?

When citing this dataset, please indicate the [release](https://github.com/OpenAPC/openapc-de/releases/) you are referring to. The releases also contain information on contributors relating to the respective release.

Please do not cite the master branch of the Github repository (https://github.com/OpenAPC/openapc-de/tree/master/), but use the release numbers/tags.

Bielefeld University Library archives a copy (including commit history). To cite:

{Contributors:} *Datasets on fee-based Open Access publishing across German Institutions*. Bielefeld University. [10.4119/UNIBI/UB.2014.18](http://dx.doi.org/10.4119/UNIBI/UB.2014.18)

## Acknowledgement

This project follows [Wellcome Trust example to share data on paid APCs](http://blog.wellcome.ac.uk/2014/03/28/the-cost-of-open-access-publishing-a-progress-report/). It recognises efforts from [JISC](https://www.jisc-collections.ac.uk/News/Releasing-open-data-about-Total-Cost-of-Ownership/) and the [ESAC initative](http://esac-initiative.org/) to standardise APC reporting. 

For data enrichment, sample visualisations and explorations we build on the work of [rOpenSci](http://ropensci.org/) and [LibreCat/Catmandu](http://librecat.org/).

## Contributors

Jens Harald Aasheim, Benjamin Ahlborn, Chelsea Ambler, Magdalena Andrae, Jochen Apel, Hans-Georg Becker, Roland Bertelmann, Daniel Beucke, Peter Blume, Ute Blumtritt, Sabine Boccalini, Kim Braun, Christoph Broschinski, Dorothea Busjahn, Pablo de Castro, Roberto Cozatl, Amanda Cullin, Patrick Danowski, Gernot Deinzer, Julia Dickel, Andrea Dorner, Stefan Drößler, Karin Eckert, Carsten Elsner, Clemens Engelhardt, Inken Feldsien-Sudhaus, Fabian Franke, Claudia Frick, Paola Galimberti, Agnes Geißelmann, Kai Karin Geschuhn, Steffi Grimm, Christian Gutknecht, Uli Hahn, Kristina Hanig, Dominik Hell, Ulrich Herb, Stephanie Herzog, Ute Holzwarth, Christie Hurrell, Doris Jaeger, Najko Jahn, Alexandra Jobmann, Andreas Kennecke, Robert Kiley, Ilka Kleinod, Lydia Koglin, Gerrit Kuehle, Ignasi Labastida i Juan, Gerald Langhanke, Stuart Lawson, Kathrin Lucht-Roussel, Jan Lüth, Frank Lützenkirchen, Anna Marini, Anja Oberländer, Jere Odell, Vitali Peil, Dirk Pieper, Tobias Pohlmann, Thomas Porquet, Markus Putnings, Annette Scheiner, Michael Schlachter, Birgit Schlegel, Stefanie Seeh, Adriana Sikora, Susanne Stemmler, Matti Stöhr, Eva Stopková, Andrée Rathemacher, Edith Reschke, Katharina Rieck, Florian Ruckelshausen, Ilka Rudolf, Marco Tullney, Astrid Vieler, Viola Voß, Marco Winkler, Sabine Witt, Philip Young

## Contact

For bugs, feature requests and other issues, please submit an issue via [Github](https://github.com/OpenAPC/openapc-de/issues/new).

For general comments, email openapc at uni-bielefeld.de

## Disclaimer

People, who are looking for "Open Advanced Process Control Software" for automation, visualization and process control tasks from home control up to industrial automation, please follow <http://www.openapc.com> (2015-09-30)
