---
layout:     post
author:		Christoph Broschinski
title:      University of Kassel updates its 2015 expenditures
date:       2016-01-26 14:00:00
summary:    
categories: [general, openAPC]
comments: true
---

```{r, echo =FALSE}

knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```


The [University of Kassel](http://www.uni-kassel.de/uni/internationales/english-version/university/about-us.html) has updated its APC expenditures for the year 2015.
The [University Library](http://www.uni-kassel.de/ub/index.php) is in charge of the [Open Access Publication Funds of the university](http://www.uni-kassel.de/ub/index.php?id=37384),
which is receiving support by the Deutsche Forschungsgemeinschaft (DFG) under its [Open-Access Publishing Programme](http://www.dfg.de/en/research_funding/programmes/infrastructure/lis/funding_opportunities/open_access_publishing/index.html).


Contact person is Dr. Tobias Pohlmann <mailto:pohlmann@bibliothek.uni-kassel.de>.

### Cost data for University of Kassel in 2015

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc_2015 <- my.apc[my.apc$institution == "Kassel U" & my.apc$period == 2015, ]
my.apc_2015 <- droplevels(my.apc_2015)
my.apc <- my.apc[my.apc$institution == "Kassel U", ]
my.apc <- droplevels(my.apc)
``````

With the recent submission, University of Kassel's APC data for the year 2015 is now complete.
2015 total expenditure amounts to `r sum(my.apc_2015$euro)`€ and the average fee is `r sum(my.apc_2015$euro)/nrow(my.apc_2015)`€. 

```{r}
my.apc_2015$journal <- factor(my.apc_2015$journal, 
                           levels =  c(rownames(data.frame(rev(sort(table(my.apc_2015$journal)))))))

df.summary <-cbind(tapply(my.apc_2015$euro, my.apc_2015$journal_full_title, length),
             tapply(my.apc_2015$euro, my.apc_2015$journal_full_title, sum),
             tapply(my.apc_2015$euro, my.apc_2015$journal_full_title, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Average Fee paid")
knitr::kable(as.data.frame(df.summary), digits = 2)
```


### Cost data for University of Kassel overall

The data set covers publication fees for `r nrow(my.apc)` Open Access journal articles. Total expenditure was `r sum(my.apc$euro)`€ and the average fee paid `r sum(my.apc$euro)/nrow(my.apc)`€.

# Fees paid per publisher (in €)

```{r tree_kassel_2015, echo=FALSE, message = FALSE}
tt <- aggregate(my.apc$euro, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

#  Average costs per year (in €)

```{r box_kassel_year_2015, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(period), euro)) + geom_boxplot() + geom_point(alpha = 8/10, size = 2,aes(colour =is_hybrid)) + scale_colour_manual(values = c("#000A02", "#DC4E00"))
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```



