---
layout:     post
author:  	Najko Jahn
title:      University Library of Ludwig-Maximilians-Universität München updates  BioMed Central expenditures

date:       2015-04-21 11:21:29
summary:    
categories: general
comments: true
---


```{r, echo = FALSE}
knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```
The [University Library of Ludwig-Maximilians-Universität München](http://www.en.ub.uni-muenchen.de/index.html) has updated [its dataset](http://openapc.github.io/general/2015/03/23/lmu/) about [author fees paid for publishing in BioMed Central journals](http://www.en.ub.uni-muenchen.de/writing/open-access-publishing/funding/index.html).

BioMed Central is part of Springer Science + Business Media.

Contact person is [Andrea Dorner](http://epub.ub.uni-muenchen.de/contact.html)


## Cost data


```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$Institution == "Muenchen LMU",]
my.apc <- droplevels(my.apc)
``````

The dataset covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles published in Springer journals by LMU Munich researchers, which the University Library covered between 2008 and 2014. Total expenditure amounts to `r sum(my.apc$EURO)`€ and the average fee is `r sum(my.apc$EURO)/nrow(my.apc)`€.


###  Average costs per year (in EURO)

```{r box_lmu_2_springer_year}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(Period), EURO)) + geom_boxplot() + geom_point(alpha = 1/10, size = 4)
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

The following table shows the distribution over BioMed Central journal titles.



```{r}
my.apc$journal <- factor(my.apc$journal, 
                           levels =  c(rownames(data.frame(rev(sort(table(my.apc$journal)))))))

df.summary <-cbind(tapply(my.apc$EURO, my.apc$journal, length),
             tapply(my.apc$EURO, my.apc$journal, sum),
             tapply(my.apc$EURO, my.apc$journal, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Average Fee paid")
knitr::kable(as.data.frame(df.summary), digits = 2)
```
