---
layout:     post
author:		Najko Jahn
title:      University of Regensburg updates dataset!
date:       2015-04-16 11:21:29
summary:    
categories: general
comments: true
---

```{r, echo =FALSE}

knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 1, digits = 2)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=" ")
})
```

[Regensburg University Library](http://www.uni-regensburg.de/library/index.html) contributes its cost information for 2014. The library is in charge of the [central publication  fund at University of Regensburg](http://oa.uni-regensburg.de/), which is supported by the DFG under its [Open-Access Publishing Programme](http://www.dfg.de/en/research_funding/programmes/infrastructure/lis/funding_opportunities/open_access_publishing/index.html).

Contact person is Dr. Gernot Deinzer <mailto:gernot.deinzer@bibliothek.uni-regensburg.de>



### Cost data

```{r, cache.lazy = TRUE}
#' Download APC spreadsheet from github which requires to Curl installed

download_apc <- function(path = NULL, dir = "tmp", file = "apc_de.csv"){
  if(is.null(path)) {
    path <- c("https://raw.githubusercontent.com/OpenAPC/openapc-de/master/data/apc_de.csv")
    } 
  dir.create(dir) 
  download.file(url = path, destfile = paste(dir, file, sep = "/"), method = "curl")
  read.csv(paste(dir, file, sep = "/"), header = T,sep =",")
}

my.apc <- download_apc()
my.apc <- my.apc[my.apc$Institution == "Regensburg U",]
my.apc <- droplevels(my.apc)
```

The dataset covers publication fees for `r format(nrow(my.apc), big.mark =",")` articles, which the fund covered between 2012 and 2014. Total expenditure amounts to `r sum(my.apc$EURO)`€ and the average fee is `r sum(my.apc$EURO)/nrow(my.apc)`€.


### Fees paid per publisher (in EURO)

```{r tree_ru}
tt <- aggregate(my.apc$EURO, by = list(my.apc$publisher), sum)
colnames(tt) <- c("Publisher", "Euro")
treemap::treemap(tt, index = c("Publisher"), vSize = "Euro", palette = "Paired")
```

###  Average costs per year (in EURO)

```{r box_ru_year, echo=FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(factor(Period), EURO)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 18)
q + xlab("Funding period") + ylab("APC")
```

###  Average costs per publisher (in EURO)

```{r box_ru_publisher, echo = FALSE, message = FALSE}
require(ggplot2)
q <- ggplot(my.apc, aes(publisher, EURO)) + geom_boxplot() + geom_point()
q <- q +  ylab("Fees paid (in EURO)") + theme(legend.position="top") + theme_bw(base_size = 12) + coord_flip()
q + xlab("Publisher") + ylab("APC")
```

The following table shows the payments the Regensburg University Library has made to the publishers (including taxes)

```{r}
my.apc$publisher <- factor(my.apc$publisher, 
                           levels =  c(rownames(data.frame(rev(sort(table(my.apc$publisher)))))))

df.summary <-cbind(tapply(my.apc$EURO, my.apc$publisher, length),
             tapply(my.apc$EURO, my.apc$publisher, sum),
             tapply(my.apc$EURO, my.apc$publisher, mean))

colnames(df.summary) <- c("Articles", "Fees paid in EURO", "Mean Fee paid")

knitr::kable(as.data.frame(df.summary), digits = 2)
```
